### 2020-07-30 README.Rmd
Initial commit

---
title: "camprotR"
output: github_document
---

### 2020-07-30 R/test_function.R
Create basic package structure
Include a dummy plotting function `test_function`.
devtools::check() runs successfully with 0 errors,
warnings, or notes.

@@ -1,0 +1,15 @@
+#' Test function
+#'
+#' Generates a scatter plot with ggplot2.
+#'
+#' @param data \code{data.frame}. Must have 2 numeric columns to plot.
+#' @param x \code{numeric}. X values to plot.
+#' @param y \code{numeric}. Y values to plot.
+#'
+#' @return ggplot using geom_point.
+#' @example inst/examples/ex-test_function.R
+#' @export
+test_function <- function(data, x, y) {
+  ggplot(data, aes(x = x, y = y)) +
+    geom_point()
+}

### 2020-07-30 inst/examples/ex-test_function.R

@@ -1,0 +1,6 @@
+df <- data.frame(
+  x = c(0, 1, 2),
+  y = c(0, 1, 2)
+)
+
+test_function(df, x, y)

### 2020-07-30 tests/testthat.R

@@ -1,0 +1,4 @@
+library(testthat)
+library(camprotR)
+
+test_check("camprotR")

### 2020-07-30 tests/testthat/test-test_function.R

@@ -1,0 +1,16 @@
+context("test_function")
+
+#### Setup ---------------------------------------------------------------------
+
+df <- data.frame(
+  x = c(0, 1, 2),
+  y = c(0, 1, 2)
+)
+
+#### Tests ---------------------------------------------------------------------
+
+test_that("test_function can create a ggplot", {
+  plot1 <- test_function(df, x, y)
+
+  expect_length(layer_grob(plot1), 1)
+})

### 2020-09-10 R/qc_plots.R
adds vingette for TMT PSM QC + summarisation

@@ -47,90 +47,3 @@ plot_quant <- function(obj,
   return(p)
 }
 
-#' Summarise percentage of tag intensities below a given threshold and missing
-#'
-#' @description Given an `MSnSet`, return a `data.frame` summarising the
-#' percentage of tag intensities below a given threshold, missing values
-#' and the median tag intensity
-#'
-#' @param obj `MSnSet`.
-#' @param threshold `numeric`. Minimum intensity threshold
-#' @param group_by_sample `logical`. Group the summaries by sample
-#'
-#' @return `data.frame` object.
-#' @export
-get_psm_metrics <- function(obj,
-                            threshold=5.75,
-                            group_by_sample=FALSE){
-  e_data <- data.frame(exprs(obj))
-
-  e_data[e_data==""] <- NA
-
-  e_data <- e_data %>% gather(key='sample', value='intensity')
-
-  if(group_by_sample){
-    e_data_grouped <- e_data %>% group_by(sample=remove_x(sample))
-    } else{
-  e_data_grouped <- e_data
-  }
-
-  e_data_grouped %>%
-    summarise(
-      missing=sum(is.na(intensity), na.rm=TRUE),
-      not_missing=sum(!is.na(intensity), na.rm=TRUE),
-      below_thresh=sum(intensity<threshold, na.rm=TRUE),
-      above_thresh=sum(intensity>=threshold, na.rm=TRUE),
-      total=missing+not_missing,
-      perc_below=round(100*below_thresh/(total),1),
-      perc_missing=round(100*missing/(total),1),
-      median_intensity=median(intensity, na.rm=TRUE)) %>%
-    ungroup
-}
-
-#' Plot histograms for TMT tag intensities per sample
-#'
-#' @description Given an `MSnSet`, return a histogram
-#' of TMT tag intensities per sample, annotated with the proportion of
-#' intensities below the upper boundary of the notch region
-#'
-#' @param obj `MSnSet`.
-#' @param notch_lower `numeric`. Lower boundary of notch.
-#' @param notch_upper `numeric`. Upper boundary of notch.
-#' @param facet_by_sample `logical`. Facet the plot by sample.
-#'
-#' @return `ggplot` object.
-#' @export
-plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sample=FALSE){
-
-  colours = get_cat_palette(2)
-
-  p <- obj %>%
-    log(base=2) %>%
[…]

### 2020-09-10 R/tmt_qc_plots.R

@@ -1,0 +1,274 @@
+#' Summarise percentage of tag intensities below a given threshold and missing
+#'
+#' @description Given an `MSnSet`, return a `data.frame` summarising the
+#' percentage of tag intensities below a given threshold, missing values
+#' and the median tag intensity
+#'
+#' @param obj `MSnSet`.
+#' @param threshold `numeric`. Minimum intensity threshold
+#' @param group_by_sample `logical`. Group the summaries by sample
+#'
+#' @return `data.frame` object.
+#' @export
+get_psm_metrics <- function(obj,
+                            threshold=5.75,
+                            group_by_sample=FALSE){
+  e_data <- data.frame(exprs(obj))
+
+  e_data[e_data==""] <- NA
+
+  e_data <- e_data %>% gather(key='sample', value='intensity')
+
+  if(group_by_sample){
+    e_data_grouped <- e_data %>% group_by(sample=remove_x(sample))
+  } else{
+    e_data_grouped <- e_data
+  }
+
+  e_data_grouped %>%
+    summarise(
+      missing=sum(is.na(intensity), na.rm=TRUE),
+      not_missing=sum(!is.na(intensity), na.rm=TRUE),
+      below_thresh=sum(intensity<threshold, na.rm=TRUE),
+      above_thresh=sum(intensity>=threshold, na.rm=TRUE),
+      total=missing+not_missing,
+      perc_below=round(100*below_thresh/(total),1),
+      perc_missing=round(100*missing/(total),1),
+      median_intensity=median(intensity, na.rm=TRUE)) %>%
+    ungroup
+}
+
+#' Plot histograms for TMT tag intensities including notch annotation
+#'
+#' @description The distribution of TMT intensities obtained by Orbitrap has
+#' been observed to have a 'notch' where few values are observed. This function
+#' returns a histogram of TMT tag intensities per sample, annotated with the
+#' proportion of intensities below the upper boundary of the notch region
+#'
+#' @param obj `MSnSet` containing PSM level TMT intensities
+#' @param notch_lower `numeric`. Lower boundary of notch.
+#' @param notch_upper `numeric`. Upper boundary of notch.
+#' @param facet_by_sample `logical`. Facet the plot by sample.
+#'
+#' @return `ggplot` object.
+#' @export
[…]

### 2020-09-10 R/tmt_qc_plots.R
reduce bins for fraction sub-notch plot

@@ -173,7 +173,7 @@ plot_fraction_below_notch_per_prot <- function(notch_per_protein){
     #filter(fraction_below>0) %>%
     mutate(sample=remove_x(sample)) %>%
     ggplot(aes(fraction_below)) +
-    geom_histogram(bins=20) +
+    geom_histogram(bins=10) +
     theme_camprot(base_size=10) +
     facet_wrap(~sample) +
     xlab('Fraction at/below notch PSMs') +

### 2020-09-11 R/camprotR-package.R
Make R CMD check pass
There is still one note:
"unable to verify current time" which can be ignored.

@@ -2,6 +2,8 @@
 "_PACKAGE"
 
 #' @import dplyr
+#' @importFrom MSnbase exprs fData
+#' @importFrom rlang .data
 #' @import tidyr
 #' @import ggplot2
 NULL

### 2020-09-11 R/combine_runs.R

@@ -1,4 +1,4 @@
-#' Extract sequence:protein ID mappings 
+#' Extract sequence:protein ID mappings
 #'
 #' @description Given a list of infiles, read the files,
 #' retain the sequence and protein ID columns and bind the rows
@@ -15,11 +15,11 @@ read_infiles <- function(infiles,
                         prot_col,
                         master_prot_col){
   seq2prot <- lapply(infiles, function(x){
-    read.delim(x, stringsAsFactors=FALSE) %>%
+    utils::read.delim(x, stringsAsFactors=FALSE) %>%
       dplyr::select(all_of(c(seq_col, prot_col, master_prot_col))) %>%
       mutate(infile=x)
   }) %>% do.call(what='rbind')
-  
+
   return(seq2prot)
 }
 
@@ -30,7 +30,7 @@ read_infiles <- function(infiles,
 #' proteins required to account for all observed sequences) to generate a
 #' single map from sequence to protein for all samples
 #'
-#' @param seq2prot `data`. Output from \code{\link{readInfiles}}
+#' @param seq2prot `data`. Output from \code{\link{read_infiles}}
 #' @param seq_col `string` Column name for peptide sequence
 #' @param prot_col `string` Column name for protein(s)
 #' @param master_prot_col `string` Column name for master protein(s)
@@ -40,60 +40,60 @@ read_infiles <- function(infiles,
 get_sequence2protein <- function(seq2prot,
                                  seq_col,
                                  prot_col){
-  
+
   # get unique seq->prot mappings
   seq_protein <- seq2prot %>%
-    separate_rows(Protein.Accessions, sep='; ') %>%
+    separate_rows(.data$Protein.Accessions, sep='; ') %>%
     dplyr::select(all_of(c(seq_col, prot_col))) %>%
     distinct()
-  
+
   protein_to_sequences <- seq_protein %>%
     group_by_at(prot_col) %>%
     summarise(Sequences=list(!!(sym(seq_col))))
-  
+
   protein_to_sequences_map <- protein_to_sequences$Sequences
-  
+
   names(protein_to_sequences_map) <- protein_to_sequences[[prot_col]]
-  
+
   protein_counts <- protein_to_sequences_map %>%
     names() %>%
     sapply(function(x) length(protein_to_sequences_map[[x]]))
-  
+
   sequences_left_to_account_for <- unique(seq_protein[[seq_col]])
   sequences_accounted_for <- NULL
[…]

### 2020-09-11 R/estimate_incorporation.R

@@ -44,7 +44,7 @@ estimate_incorporation <- function(psm_infile,
                                    outdir) {
   if (!dir.exists(outdir)) dir.create(outdir)
 
-  psm_sequenced_data <- silac_psm_seq_int(read.delim(psm_infile),
+  psm_sequenced_data <- silac_psm_seq_int(utils::read.delim(psm_infile),
     sequence_col = sequence_col
   )
 
@@ -57,7 +57,7 @@ estimate_incorporation <- function(psm_infile,
     stringr::str_extract_all("(?<=\\|).*?(?=\\|)") %>%
     unlist()
 
-  peptide_data <- parse_features(read.delim(peptide_infile),
+  peptide_data <- parse_features(utils::read.delim(peptide_infile),
     master_protein_col = master_protein_col,
     protein_col = protein_col,
     unique_master = FALSE,
@@ -68,7 +68,7 @@ estimate_incorporation <- function(psm_infile,
     filter_associated_crap = TRUE
   ) %>%
     filter(grepl('K|R|k|r', !!sym(sequence_col))) %>%
-    filter(Quan.Info != 'Redundant')
+    filter(.data$Quan.Info != 'Redundant')
 
   light_col <- colnames(peptide_data)[
     grepl('Abundances.Grouped.(F\\d*.)?Light', colnames(peptide_data))
@@ -79,31 +79,31 @@ estimate_incorporation <- function(psm_infile,
 
   peptide_data <- peptide_data %>%
     select(!!sym(sequence_col), !!sym(modifications_col),
-      !!sym(protein_col), !!sym(master_protein_col), Number.of.Missed.Cleavages,
+      !!sym(protein_col), !!sym(master_protein_col), .data$Number.of.Missed.Cleavages,
       'light' = all_of(light_col), 'heavy' = all_of(heavy_col)
     ) %>%
-    mutate(corrected_light = light - (mix * heavy)) %>%
+    mutate(corrected_light = .data$light - (mix * .data$heavy)) %>%
     rowwise() %>%
     mutate(
-      incorporation = get_incorporation(light, heavy),
-      corrected_incorporation = get_incorporation(corrected_light, heavy)
+      incorporation = get_incorporation(.data$light, .data$heavy),
+      corrected_incorporation = get_incorporation(.data$corrected_light, .data$heavy)
     )
 
   peptide_data <- peptide_data %>%
     remove_silac_modifications(level = 'peptide') %>%
[…]

### 2020-09-11 R/extract_psm_info.R

@@ -15,21 +15,21 @@
 silac_psm_seq_int <- function(obj, sequence_col='Sequence'){
 
   obj <- obj %>%
-    filter(Quan.Channel!='') %>%
+    filter(.data$Quan.Channel!='') %>%
     rowwise() %>%
-    filter(is.finite(Precursor.Abundance)) %>%
+    filter(is.finite(.data$Precursor.Abundance)) %>%
     remove_silac_modifications(level='psm') %>%
-    mutate(Modifications=psm_to_peptide_style_modifications(Modifications))
+    mutate(Modifications=psm_to_peptide_style_modifications(.data$Modifications))
 
   obj_seq <- obj %>%
-    group_by(!!sym(sequence_col), Quan.Channel, Modifications) %>%
-    summarise(sequenced=any(is.finite(Precursor.Abundance))) %>%
-    mutate(Quan.Channel=paste0('Sequenced_', Quan.Channel)) %>%
-    spread(key=Quan.Channel, value=sequenced, fill=FALSE)
+    group_by(!!sym(sequence_col), .data$Quan.Channel, .data$Modifications) %>%
+    summarise(sequenced=any(is.finite(.data$Precursor.Abundance))) %>%
+    mutate(Quan.Channel=paste0('Sequenced_', .data$Quan.Channel)) %>%
+    spread(key=.data$Quan.Channel, value=.data$sequenced, fill=FALSE)
 
   obj_int <- obj %>%
-    group_by(!!sym(sequence_col), Modifications) %>%
-    summarise(max_interference=max(Isolation.Interference.in.Percent))
+    group_by(!!sym(sequence_col), .data$Modifications) %>%
+    summarise(max_interference=max(.data$Isolation.Interference.in.Percent))
 
   obj_seq_int<- merge(obj_seq, obj_int, by=c(sequence_col, 'Modifications'))
 

### 2020-09-11 R/modifications.R

@@ -7,11 +7,11 @@
 #' more succintly, with the number of each modification followed by the positions
 #' For example:
 #' PSM: N-Term(Prot)(Acetyl); C2(Carbamidomethyl); C16(Carbamidomethyl)
-#' Peptide:1xAcetyl [N-Term]; 2xCarbamidomethyl [C2; C16]
+#' Peptide:1xAcetyl \[N-Term\]; 2xCarbamidomethyl \[C2; C16\]
 #'
-#' @param obj `vector` of PSM-style modification annotations
+#' @param psm_style_modifications `vector` of PSM-style modification annotations
 #' @return `vector` of Peptide-style modification annotations
-#' @example
+#' @examples
 #' psm_mod <- "N-Term(Prot)(Acetyl); C2(Carbamidomethyl); C16(Carbamidomethyl)"
 #' target <- "1xAcetyl [N-Term]; 2xCarbamidomethyl [C2; C16]"
 #' psm_to_peptide_style_modifications(psm_mod)==target

### 2020-09-11 R/qc_plots.R

@@ -22,20 +22,20 @@ plot_quant <- function(obj,
 
   if(method=='box'){
     p <- p +
-      geom_boxplot(aes(sample, intensity)) +
+      geom_boxplot(aes(sample, .data$intensity)) +
       theme(axis.text.x=element_text(angle=45, vjust=1, hjust=1)) +
       ylab("Feature intensity") +
       xlab("")
   }
   else if(method=='density'){
     p <- p +
-      geom_density(aes(intensity, col=sample)) +
+      geom_density(aes(.data$intensity, col=sample)) +
       xlab("Feature intensity") +
       ylab("Density")
   }
   else if(method=='histogram'){
     p <- p +
-      geom_histogram(aes(intensity), bins=100) +
+      geom_histogram(aes(.data$intensity), bins=100) +
       scale_y_continuous(expand = c(0, 0)) +
       xlab("Feature intensity") +
       ylab("Count")
@@ -76,15 +76,15 @@ get_psm_metrics <- function(obj,
 
   e_data_grouped %>%
     summarise(
-      missing=sum(is.na(intensity), na.rm=TRUE),
-      not_missing=sum(!is.na(intensity), na.rm=TRUE),
-      below_thresh=sum(intensity<threshold, na.rm=TRUE),
-      above_thresh=sum(intensity>=threshold, na.rm=TRUE),
-      total=missing+not_missing,
-      perc_below=round(100*below_thresh/(total),1),
-      perc_missing=round(100*missing/(total),1),
-      median_intensity=median(intensity, na.rm=TRUE)) %>%
-    ungroup
+      missing=sum(is.na(.data$intensity), na.rm=TRUE),
+      not_missing=sum(!is.na(.data$intensity), na.rm=TRUE),
+      below_thresh=sum(.data$intensity<threshold, na.rm=TRUE),
+      above_thresh=sum(.data$intensity>=threshold, na.rm=TRUE),
+      total=.data$missing+.data$not_missing,
+      perc_below=round(100*.data$below_thresh/(.data$total),1),
+      perc_missing=round(100*.data$missing/(.data$total),1),
+      median_intensity=stats::median(.data$intensity, na.rm=TRUE)) %>%
+    ungroup()
 }
 
 #' Plot histograms for TMT tag intensities per sample
@@ -114,9 +114,9 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
 
   if(facet_by_sample){
[…]

### 2020-09-11 R/silac.R

@@ -42,7 +42,9 @@ get_incorporation <- function(light, heavy){
 #' @param obj `data.frame` containing features with column 'incorporation'.
 #' If mix>0, must also contain column 'corrected_incorporation' where incorporation
 #' is calculated using the corrected light peptide intensity
-#' @param level `string` Name for feature level. e.g 'Peptide' or 'Protein'
+#' @param level `string`. Name for feature level. e.g 'Peptide' or 'Protein'
+#' @param mix `numeric`. Default is 0. Otherwise use a number greater than zero
+#' (i.e. the 'Heavy' to 'Light' mix ratio).
 #' @return `list` with `p`=`ggplot` plot and `incorporation_estimates`=`list` of
 #' incorporation estimates
 #' @export
@@ -50,7 +52,7 @@ plot_incorporation <- function(obj, level='Peptide', mix=0){
 
   p <- obj %>%
     ggplot() +
-    geom_histogram(aes(100*incorporation), fill='grey') +
+    geom_histogram(aes(100*.data$incorporation), fill='grey') +
     theme_camprot(base_size=10) +
     xlab('Observed incorporation (%)') +
     ylab('Count')
@@ -60,13 +62,13 @@ plot_incorporation <- function(obj, level='Peptide', mix=0){
   if(mix>0){
 
     median_incorporation <- obj %>%
-      pull(incorporation) %>%
-      median(na.rm=TRUE) %>%
+      pull(.data$incorporation) %>%
+      stats::median(na.rm=TRUE) %>%
       "*"(100)
 
     median_corrected_incorporation <- obj %>%
-      pull(corrected_incorporation) %>%
-      median(na.rm=TRUE) %>%
+      pull(.data$corrected_incorporation) %>%
+      stats::median(na.rm=TRUE) %>%
       "*"(100)
 
     incorporation_estimates <- list(
@@ -82,12 +84,12 @@ plot_incorporation <- function(obj, level='Peptide', mix=0){
 
   } else{
     median_incorporation <- obj %>%
-      pull(incorporation) %>%
-      median(na.rm=TRUE) %>%
+      pull(.data$incorporation) %>%
+      stats::median(na.rm=TRUE) %>%
       "*"(100)
 
     mean_incorporation <- obj %>%
-      pull(incorporation) %>%
+      pull(.data$incorporation) %>%
       mean(na.rm=TRUE) %>%
       "*"(100)
 

### 2020-09-11 R/camprotR-package.R
Change Msnbase to Biobase import for now

@@ -2,7 +2,7 @@
 "_PACKAGE"
 
 #' @import dplyr
-#' @importFrom MSnbase exprs fData
+#' @importFrom Biobase exprs fData
 #' @importFrom rlang .data
 #' @import tidyr
 #' @import ggplot2

### 2020-09-28 R/extract_psm_info.R
updates extract_psm_info to handle input with SILAC modifications and/or annotated sequence column

@@ -23,9 +23,12 @@ silac_psm_seq_int <- function(
   obj <- obj %>%
     filter(.data$Quan.Channel!='') %>%
     rowwise() %>%
-    filter(is.finite(.data$Precursor.Abundance)) %>%
-    # mutate(mod_col=remove_silac_modifications(!!sym(mod_col), level='psm')) %>%
-    mutate(mod_col=psm_to_peptide_style_modifications(!!sym(mod_col)))
+    filter(is.finite(.data$Precursor.Abundance))
+
+  obj[[mod_col]] <- remove_silac_modifications(obj[[mod_col]])
+  obj[[mod_col]] <- psm_to_peptide_style_modifications(obj[[mod_col]])
+
+  obj[[sequence_col]] <- toupper(obj[[sequence_col]])
 
   obj_seq <- obj %>%
     group_by(!!sym(sequence_col), .data$Quan.Channel, !!sym(mod_col)) %>%
@@ -42,5 +45,4 @@ silac_psm_seq_int <- function(
 
   return(obj_seq_int)
 }
-
 

### 2020-09-28 R/qc_plots.R
removes duplicated functions

@@ -47,90 +47,6 @@ plot_quant <- function(obj,
   return(p)
 }
 
-#' Summarise percentage of tag intensities below a given threshold and missing
-#'
-#' @description Given an `MSnSet`, return a `data.frame` summarising the
-#' percentage of tag intensities below a given threshold, missing values
-#' and the median tag intensity
-#'
-#' @param obj `MSnSet`.
-#' @param threshold `numeric`. Minimum intensity threshold
-#' @param group_by_sample `logical`. Group the summaries by sample
-#'
-#' @return `data.frame` object.
-#' @export
-get_psm_metrics <- function(obj,
-                            threshold=5.75,
-                            group_by_sample=FALSE){
-  e_data <- data.frame(exprs(obj))
 
-  e_data[e_data==""] <- NA
 
-  e_data <- e_data %>% gather(key='sample', value='intensity')
 
-  if(group_by_sample){
-    e_data_grouped <- e_data %>% group_by(sample=remove_x(sample))
-    } else{
-  e_data_grouped <- e_data
-  }
-
-  e_data_grouped %>%
-    summarise(
-      missing=sum(is.na(.data$intensity), na.rm=TRUE),
-      not_missing=sum(!is.na(.data$intensity), na.rm=TRUE),
-      below_thresh=sum(.data$intensity<threshold, na.rm=TRUE),
-      above_thresh=sum(.data$intensity>=threshold, na.rm=TRUE),
-      total=.data$missing+.data$not_missing,
-      perc_below=round(100*.data$below_thresh/(.data$total),1),
-      perc_missing=round(100*.data$missing/(.data$total),1),
-      median_intensity=stats::median(.data$intensity, na.rm=TRUE)) %>%
-    ungroup()
-}
-
-#' Plot histograms for TMT tag intensities per sample
-#'
-#' @description Given an `MSnSet`, return a histogram
-#' of TMT tag intensities per sample, annotated with the proportion of
-#' intensities below the upper boundary of the notch region
-#'
-#' @param obj `MSnSet`.
-#' @param notch_lower `numeric`. Lower boundary of notch.
-#' @param notch_upper `numeric`. Upper boundary of notch.
-#' @param facet_by_sample `logical`. Facet the plot by sample.
-#'
-#' @return `ggplot` object.
-#' @export
[…]

### 2020-09-28 R/tmt_qc_plots.R
address R CMD check warnings re global variables due to tidyverse non-standard evaluation

@@ -93,17 +93,17 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
 #' been observed to have a 'notch' where few values are observed. This function
 #' summarises the number of sub-notch values observed per protein
 #'
-#' @param obj `MSnSet` containing PSM level TMT intensities.
+#' @param obj `MSnSet` containing PSM-level TMT intensities.
 #' @param notch_upper `numeric`. Upper boundary of notch.
-#' @param master_protein_col `character`. Column name for master proteins.
+#' @param master_prot_col `character`. Column name for master proteins.
 #'
 #' @return `data.frame` Summarises # PSMs above/below notch for each protein
 #' @export
-get_notch_per_protein <- function(.psm,
+get_notch_per_protein <- function(obj,
                                   master_prot_col='Master.Protein.Accessions',
                                   notch_upper=5.75){
 
-  retain_prot <- .psm %>%
+  retain_prot <- obj %>%
     fData() %>%
     group_by_at(master_prot_col) %>%
     tally() %>%
@@ -112,15 +112,15 @@ get_notch_per_protein <- function(.psm,
 
   notch_per_protein <- data.frame(exprs(.psm)<log2(notch_upper)) %>%
     merge(fData(.psm)[,master_prot_col, drop=FALSE], by='row.names') %>%
-    gather(key='sample', value='below_notch', -c(Row.names, !!sym(master_prot_col))) %>%
+    gather(key='sample', value='below_notch', -c(.data$Row.names, !!sym(master_prot_col))) %>%
     filter(!!sym(master_prot_col) %in% retain_prot) %>%
-    filter(!is.na(below_notch)) %>%
+    filter(!is.na(.data$below_notch)) %>%
     #tibble::rownames_to_column('sample') %>%
     group_by(!!sym(master_prot_col), sample) %>%
-    summarise(n_psm=length(below_notch),
-              n_below=sum(below_notch),
-              fraction_below=n_below/n_psm) %>%
-    arrange(desc(fraction_below))
+    summarise(n_psm=length(.data$below_notch),
+              n_below=sum(.data$below_notch),
+              fraction_below=.data$n_below/.data$n_psm) %>%
+    arrange(desc(.data$fraction_below))
 
   return(notch_per_protein)
 }
[…]

### 2020-09-28 R/tmt_qc_plots.R
debug get_notch_per_protein

@@ -110,8 +110,8 @@ get_notch_per_protein <- function(obj,
     filter(n>1) %>%
     pull(!!sym(master_prot_col))
 
-  notch_per_protein <- data.frame(exprs(.psm)<log2(notch_upper)) %>%
-    merge(fData(.psm)[,master_prot_col, drop=FALSE], by='row.names') %>%
+  notch_per_protein <- data.frame(exprs(obj)<log2(notch_upper)) %>%
+    merge(fData(obj)[,master_prot_col, drop=FALSE], by='row.names') %>%
     gather(key='sample', value='below_notch', -c(.data$Row.names, !!sym(master_prot_col))) %>%
     filter(!!sym(master_prot_col) %in% retain_prot) %>%
     filter(!is.na(.data$below_notch)) %>%

### 2020-09-29 R/qc_plots.R
debugs plot_quant for samples with names starting with numeric character

@@ -16,7 +16,7 @@ plot_quant <- function(obj,
 
   e_data[e_data==""] <- NA
   e_data <- e_data %>% gather(key='sample', value='intensity') %>%
-    mutate(sample=factor(remove_x(sample), levels=colnames(e_data)))
+    mutate(sample = factor(remove_x(sample), levels = remove_x(colnames(e_data))))
 
   p <- ggplot(e_data) + theme_bw()
 

### 2020-09-30 R/ptm.R
debugs add_PTM_positions

@@ -166,7 +166,7 @@ add_PTM_positions <- function(obj, proteome_fasta, master_protein_col = "Master.
       return("")
     }
 
-    peptide_starts <- stats::start(Biostrings::matchPattern(sequence, proteome[[protein]]))
+    peptide_starts <- Biostrings::start(Biostrings::matchPattern(sequence, proteome[[protein]]))
 
     for (p_start in peptide_starts) {
       position_string <- NULL
@@ -321,8 +321,8 @@ add_peptide_positions <- function(obj,
     if (!protein %in% names(proteome)) {
       return(c(NA, NA))
     }
-    peptide_start <- stats::start(Biostrings::matchPattern(sequence, proteome[[protein]]))
-    peptide_end <- stats::end(Biostrings::matchPattern(sequence, proteome[[protein]]))
+    peptide_start <- Biostrings::start(Biostrings::matchPattern(sequence, proteome[[protein]]))
+    peptide_end <- Biostrings::end(Biostrings::matchPattern(sequence, proteome[[protein]]))
 
     if (length(peptide_start) != 1) {
       return(c(NA, NA))

### 2020-09-30 R/tmt_qc_plots.R
addresses R CMD check warnings

@@ -27,14 +27,14 @@ get_psm_metrics <- function(obj,
 
   e_data_grouped %>%
     summarise(
-      missing=sum(is.na(intensity), na.rm=TRUE),
-      not_missing=sum(!is.na(intensity), na.rm=TRUE),
-      below_thresh=sum(intensity<threshold, na.rm=TRUE),
-      above_thresh=sum(intensity>=threshold, na.rm=TRUE),
-      total=missing+not_missing,
-      perc_below=round(100*below_thresh/(total),1),
-      perc_missing=round(100*missing/(total),1),
-      median_intensity=median(intensity, na.rm=TRUE)) %>%
+      missing=sum(is.na(.data$intensity), na.rm=TRUE),
+      not_missing=sum(!is.na(.data$intensity), na.rm=TRUE),
+      below_thresh=sum(.data$intensity<threshold, na.rm=TRUE),
+      above_thresh=sum(.data$intensity>=threshold, na.rm=TRUE),
+      total=.data$missing+.data$not_missing,
+      perc_below=round(100*.data$below_thresh/(.data$total),1),
+      perc_missing=round(100*.data$missing/(.data$total),1),
+      median_intensity=stats::median(.data$intensity, na.rm=TRUE)) %>%
     ungroup
 }
 
@@ -66,7 +66,7 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
 
   if(facet_by_sample){
     psm_metrics <- get_psm_metrics(obj, threshold=notch_upper, group_by_sample=TRUE) %>%
-      mutate(label=sprintf('%s %%  ', perc_below))
+      mutate('label'=sprintf('%s %%  ', .data$perc_below))
 
     p <- p + geom_text(aes(label=label), data=psm_metrics,
                        family='serif',
@@ -141,10 +141,10 @@ get_notch_per_protein <- function(obj,
 plot_below_notch_per_prot <- function(notch_per_protein){
 
   p_notch_per_protein <- notch_per_protein %>%
-    group_by(n_below, sample=remove_x(sample)) %>%
+    group_by(.data$n_below, sample=remove_x(.data$sample)) %>%
     tally() %>%
     ggplot(aes(sample, n, fill=Hmisc::cut2(
-      n_below, cuts=c(0, 1, 3, 5, 8, 12, 20, 43)))) +
+      .data$n_below, cuts=c(0, 1, 3, 5, 8, 12, 20, 43)))) +
     geom_bar(stat='identity', position='fill') +
[…]

### 2020-10-01 R/tmt_qc_plots.R
resolves R CMD check warnings

@@ -66,9 +66,9 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
 
   if(facet_by_sample){
     psm_metrics <- get_psm_metrics(obj, threshold=notch_upper, group_by_sample=TRUE) %>%
-      mutate('label'=sprintf('%s %%  ', .data$perc_below))
+      mutate(label=sprintf('%s %%  ', .data$perc_below))
 
-    p <- p + geom_text(aes(label=label), data=psm_metrics,
+    p <- p + geom_text(aes(label=.data$label), data=psm_metrics,
                        family='serif',
                        x=log2(notch_lower), y=Inf,
                        vjust=2, hjust=1, size=4) +
@@ -194,6 +194,7 @@ plot_fraction_below_notch_per_prot <- function(notch_per_protein){
 #'
 #' @return `ggplot` stacked bar plot to show S:N vs # missing values
 #' @export
+#' @importFrom grDevices colorRampPalette
 plot_missing_SN <- function(obj,
                           sn_column="Average.Reporter.SN",
                           bins=20){
@@ -204,11 +205,11 @@ plot_missing_SN <- function(obj,
 
   p <- data.frame('n_missing'=n_missing,
                   'sn'=fData(obj)[[sn_column]]) %>%
-    mutate(binned_sn=Hmisc::cut2(sn, g=bins, digits=1)) %>%
-    filter(is.finite(sn)) %>%
-    group_by(n_missing, binned_sn) %>%
+    mutate(binned_sn=Hmisc::cut2(.data$sn, g=bins, digits=1)) %>%
+    filter(is.finite(.data$sn)) %>%
+    group_by(.data$n_missing, .data$binned_sn) %>%
     tally() %>%
-    ggplot(aes(binned_sn, n, fill=factor(n_missing))) +
+    ggplot(aes(.data$binned_sn, n, fill=factor(n_missing))) +
     geom_bar(stat='identity', position='fill', colour='grey20', lwd=0.1) +
     scale_fill_manual(values=c('grey70', pal(max(n_missing))), name='Missing values') +
     guides(colour=guide_legend(override.aes = list(size = 1.5))) +
@@ -250,12 +251,12 @@ plot_missing_SN_per_sample <- function(obj,
 
   p <- sn_per_sample %>%
     group_by(.data$sample, .data$binned_sn,
-             missing=ifelse(is.na(value), 'missing', 'present')) %>%
[…]

### 2020-10-01 tests/testthat/test-notch_per_protein.R
adds tests for notch_per_protein & parse_features

@@ -1,0 +1,8 @@
+context('Tallying sub-notch values in PSM-level TMT data')
+
+test_that("Extract info", {
+  data('psm_data_notch_count', package='camprotR')
+  expect_equal_to_reference(get_notch_per_protein(psm_data_notch_count), 'notch_count.rds')
+})
+
+

### 2020-10-02 R/tmt_qc_plots.R
update notch plotting

@@ -79,8 +79,8 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
     p <- p + annotate(geom='text',
                       label=sprintf('%s %%  ', psm_metrics$perc_below),
                       family='serif',
-                      x=log2(notch_lower), y=Inf,
-                      vjust=2, hjust=1, size=8) +
+                      x=log2(max(exprs(obj), na.rm=TRUE)), y=Inf,
+                      vjust=2, hjust=1, size=5) +
       theme_camprot(border=FALSE)
   }
 

### 2020-10-05 R/tmt_qc_plots.R
Minor formatting changes
Also remove redundant scale change from plot_TMT_notch

@@ -59,7 +59,6 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
   p <- obj %>%
     log(base=2) %>%
     plot_quant(method='histogram', facet_by_sample=facet_by_sample) +
-    scale_y_continuous(expand = c(0, 0)) +
     xlab('PSM intensity (log2)') +
     geom_vline(xintercept=log2(notch_lower), size=0.5, colour=colours[2]) +
     geom_vline(xintercept=log2(notch_upper), size=0.5, colour=colours[1])
@@ -84,7 +83,7 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
       theme_camprot(border=FALSE)
   }
 
-  invisible(p)
+  return(p)
 }
 
 #' Summarise the number of sub-notch PSM intensities per protein
@@ -218,7 +217,7 @@ plot_missing_SN <- function(obj,
     theme_camprot(base_size=12, border=FALSE) +
     theme(axis.text.x=element_text(size=10, angle=45, vjust=1, hjust=1))
 
-  invisible(p)
+  return(p)
 
 }
 

### 2020-10-05 R/match_id.R
Test match_id

@@ -13,7 +13,8 @@
 #' @param match `string`. Name of column in `ref` to use for
 #' matching.
 #' @param new `character vector`. Name of column(s) in `ref` to bind
-#' to `data`.
+#' to `data`. If not character columns, they will be coerced to class character
+#' with a warning.
 #' @param regex `string`. Regular expression to use for extracting the IDs
 #' from the `to_match` column in `data`.
 #' @param collapse `string`. If there are multiple IDs in the
@@ -110,6 +111,14 @@ match_id_ <- function(to_match, ref, match, new,
       Map("[", list(as.character(ref[[x]])), matched_list)
     }, simplify = FALSE
   )
+
+  # compare class of columns from reference to columns of result to identify
+  # any unwanted type conversion i.e. numeric to character.
+  class_ref <- lapply(new, function(x) class(ref[[x]]))
+
+  if(any(class_ref != "character")) {
+    warning("Some of the column(s) specified by 'new' have been coerced to class 'character'")
+  }
 
   # collapse multiple matches so the length is the same as match_col
   result <- lapply(new_cols, function(x) sapply(x, function(y) paste(y, collapse = ";")))

### 2020-10-06 R/tmt_qc_plots.R
updates per-sample tmt notch plot

@@ -69,8 +69,8 @@ plot_TMT_notch <- function(obj, notch_lower=3.75, notch_upper=5.75, facet_by_sam
 
     p <- p + geom_text(aes(label=.data$label), data=psm_metrics,
                        family='serif',
-                       x=log2(notch_lower), y=Inf,
-                       vjust=2, hjust=1, size=4) +
+                       x=log2(max(exprs(obj), na.rm=TRUE)), y=Inf,
+                       vjust=2, hjust=1, size=3) +
       theme_camprot(border=FALSE, base_size=10)
   } else{
     psm_metrics <- get_psm_metrics(obj, threshold=notch_upper)

### 2020-10-06 R/qc_plots.R
{ts} add vignette tmt qc (#12)
* adds vingette for TMT PSM QC + summarisation

* reduce bins for fraction sub-notch plot

* debug DESCRIPTION post conflict-resolution

* updates explanation in TMT QC vignette

* updates docs for get_psm_metrics

* removes duplicated functions

* renames vignette

* makes package build include vignettes

* address R CMD check warnings re global variables due to tidyverse non-standard evaluation

* updates docs aftere addressing R CMD check warnings

* debug get_notch_per_protein

* update vignette explanation

* debugs plot_quant for samples with names starting

@@ -16,7 +16,7 @@ plot_quant <- function(obj,
 
   e_data[e_data==""] <- NA
   e_data <- e_data %>% gather(key='sample', value='intensity') %>%
-    mutate(sample=factor(remove_x(sample), levels=colnames(e_data)))
+    mutate(sample = factor(remove_x(sample), levels = remove_x(colnames(e_data))))
 
   p <- ggplot(e_data) + theme_bw()
 
@@ -47,90 +47,6 @@ plot_quant <- function(obj,
   return(p)
 }
 
-#' Summarise percentage of tag intensities below a given threshold and missing
-#'
-#' @description Given an `MSnSet`, return a `data.frame` summarising the
-#' percentage of tag intensities below a given threshold, missing values
-#' and the median tag intensity
-#'
-#' @param obj `MSnSet`.
-#' @param threshold `numeric`. Minimum intensity threshold
-#' @param group_by_sample `logical`. Group the summaries by sample
-#'
-#' @return `data.frame` object.
-#' @export
-get_psm_metrics <- function(obj,
-                            threshold=5.75,
-                            group_by_sample=FALSE){
-  e_data <- data.frame(exprs(obj))
 
-  e_data[e_data==""] <- NA
 
-  e_data <- e_data %>% gather(key='sample', value='intensity')
 
-  if(group_by_sample){
-    e_data_grouped <- e_data %>% group_by(sample=remove_x(sample))
-    } else{
-  e_data_grouped <- e_data
-  }
-
-  e_data_grouped %>%
-    summarise(
-      missing=sum(is.na(.data$intensity), na.rm=TRUE),
-      not_missing=sum(!is.na(.data$intensity), na.rm=TRUE),
-      below_thresh=sum(.data$intensity<threshold, na.rm=TRUE),
-      above_thresh=sum(.data$intensity>=threshold, na.rm=TRUE),
-      total=.data$missing+.data$not_missing,
-      perc_below=round(100*.data$below_thresh/(.data$total),1),
-      perc_missing=round(100*.data$missing/(.data$total),1),
-      median_intensity=stats::median(.data$intensity, na.rm=TRUE)) %>%
-    ungroup()
-}
-
-#' Plot histograms for TMT tag intensities per sample
-#'
-#' @description Given an `MSnSet`, return a histogram
-#' of TMT tag intensities per sample, annotated with the proportion of
[…]

### 2020-10-06 R/tmt_qc_plots.R

@@ -1,0 +1,273 @@
+#' Summarise percentage of tag intensities below a given threshold and missing
+#'
+#' @description Given an `MSnSet`, return a `data.frame` summarising the
+#' percentage of tag intensities below a given threshold, missing values
+#' and the median tag intensity
+#'
+#' @param obj `MSnSet`.
+#' @param threshold `numeric`. Minimum intensity threshold
+#' @param group_by_sample `logical`. Group the summaries by sample
+#'
+#' @return `data.frame` object.
+#' @export
+get_psm_metrics <- function(obj,
+                            threshold=5.75,
+                            group_by_sample=FALSE){
+  e_data <- data.frame(exprs(obj))
+
+  e_data[e_data==""] <- NA
+
+  e_data <- e_data %>% gather(key='sample', value='intensity')
+
+  if(group_by_sample){
+    e_data_grouped <- e_data %>% group_by(sample=remove_x(sample))
+  } else{
+    e_data_grouped <- e_data
+  }
+
+  e_data_grouped %>%
+    summarise(
+      missing=sum(is.na(.data$intensity), na.rm=TRUE),
+      not_missing=sum(!is.na(.data$intensity), na.rm=TRUE),
+      below_thresh=sum(.data$intensity<threshold, na.rm=TRUE),
+      above_thresh=sum(.data$intensity>=threshold, na.rm=TRUE),
+      total=.data$missing+.data$not_missing,
+      perc_below=round(100*.data$below_thresh/(.data$total),1),
+      perc_missing=round(100*.data$missing/(.data$total),1),
+      median_intensity=stats::median(.data$intensity, na.rm=TRUE)) %>%
+    ungroup
+}
+
+#' Plot histograms for TMT tag intensities including notch annotation
+#'
+#' @description The distribution of TMT intensities obtained by Orbitrap has
+#' been observed to have a 'notch' where few values are observed. This function
+#' returns a histogram of TMT tag intensities per sample, annotated with the
+#' proportion of intensities below the upper boundary of the notch region
+#'
+#' @param obj `MSnSet` containing PSM level TMT intensities
+#' @param notch_lower `numeric`. Lower boundary of notch.
+#' @param notch_upper `numeric`. Upper boundary of notch.
+#' @param facet_by_sample `logical`. Facet the plot by sample.
+#'
+#' @return `ggplot` object.
[…]

### 2020-10-06 tests/testthat/test-parse_features.R

@@ -1,5 +1,21 @@
-context("parse_features")
+context("Parsing PSM level PD output for TMT data")
 
 #### Setup ---------------------------------------------------------------------
+psm_data <- read.delim(
+  system.file("extdata", "TMT_PSMs.txt.gz", package = "camprotR"),
+  stringsAsFactors=FALSE)
+
+crap_fasta_inf <- system.file("extdata", "cRAP_FullIdentifiers.fasta.gz",
+                              package = "camprotR")
+
+# Load the cRAP FASTA used for the PD search
+crap.fasta <- Biostrings::fasta.index(crap_fasta_inf, seqtype = "AA")
+
+# Extract the non cRAP UniProt accessions associated with each cRAP protein
+crap.accessions <- unlist(
+  stringr::str_extract_all(crap.fasta$desc, "(?<=\\|).*?(?=\\|)"))
 
 #### Tests ---------------------------------------------------------------------
+out <- camprotR::parse_features(psm_data, TMT=TRUE, level='PSM',
+                                crap_proteins=crap.accessions)
+expect_equal_to_reference(out, file='parsed_tmt_psm.rds')

### 2021-01-28 R/estimate_incorporation.R
remove dependencies (#17)
* Move stringr to suggests

* Replace Hmisc with cutr

@@ -54,7 +54,7 @@ estimate_incorporation <- function(psm_infile,
   # Extract the non cRAP UniProt accessions associated with each cRAP protein
   crap.accessions <- crap.fasta %>%
     pull(desc) %>%
-    stringr::str_extract_all("(?<=\\|).*?(?=\\|)") %>%
+    regmatches(.data, gregexpr("(?<=\\|).*?(?=\\|)", .data, perl = TRUE)) %>%
     unlist()
 
   peptide_data <- parse_features(utils::read.delim(peptide_infile),

### 2021-01-28 R/tmt_qc_plots.R

@@ -142,7 +142,7 @@ plot_below_notch_per_prot <- function(notch_per_protein){
   p_notch_per_protein <- notch_per_protein %>%
     group_by(.data$n_below, sample=remove_x(.data$sample)) %>%
     tally() %>%
-    ggplot(aes(sample, n, fill=Hmisc::cut2(
+    ggplot(aes(sample, n, fill=cutr::cutf2(
       .data$n_below, cuts=c(0, 1, 3, 5, 8, 12, 20, 43)))) +
     geom_bar(stat='identity', position='fill') +
     scale_fill_manual(name='# PSMs below notch', values=c('grey', get_cat_palette(6))) +
@@ -204,7 +204,7 @@ plot_missing_SN <- function(obj,
 
   p <- data.frame('n_missing'=n_missing,
                   'sn'=fData(obj)[[sn_column]]) %>%
-    mutate(binned_sn=Hmisc::cut2(.data$sn, g=bins, digits=1)) %>%
+    mutate(binned_sn=cutr::cutf2(.data$sn, g=bins, digits=1)) %>%
     filter(is.finite(.data$sn)) %>%
     group_by(.data$n_missing, .data$binned_sn) %>%
     tally() %>%
@@ -246,7 +246,7 @@ plot_missing_SN_per_sample <- function(obj,
     merge(fData(obj)[,sn_column, drop=FALSE], by.x='PSM_id', by.y='row.names') %>%
     filter(is.finite(.data$Average.Reporter.SN))
 
-  sn_per_sample$binned_sn <- Hmisc::cut2(sn_per_sample[[sn_column]], g=bins, digits=1)
+  sn_per_sample$binned_sn <- cutr::cutf2(sn_per_sample[[sn_column]], g=bins, digits=1)
 
   p <- sn_per_sample %>%
     group_by(.data$sample, .data$binned_sn,

### 2021-01-28 README.Rmd
Remove travis
Use github actions for R CMD check

@@
 ---
+
+<!-- badges: start -->
+[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
+[![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR)
+<!-- badges: end -->

### 2021-01-28 README.Rmd
Update codecov

--- 2020-07-30 README.Rmd
@@
 ---
+
+<!-- badges: start -->
+[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
+[![Codecov test coverage](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR?branch=master)
+<!-- badges: end -->

### 2021-02-01 README.Rmd
Fix codecov badge

--- 2020-07-30 README.Rmd
@@
 ---
+
+<!-- badges: start -->
+[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
+[![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR?branch=master)
+<!-- badges: end -->

### 2021-02-01 R/filter_TMT_PSMs.R
Drop travis (#18)
Merge some commits from master:
* adds functions to update ave. S/N, count features per protein & center-normalise
* adds test for center-median normalisation function
* updates test descriptions
* debug update_average_sn test bug
* gobbles up some low-hanging testing fruit (#13)
* gobbles up some low-haning testing fruit
* Test match_id
* Add filter_x tests
* rectifies typo
* Don't use devtools::check()
* remove dependencies (#17)
* Move stringr to suggests
* Replace Hmisc with cutr

Merge drop_travis branch:
* Remove travis
* Use github actions for R CMD check
* Update code

@@ -1,3 +1,24 @@
+#' Adds new feature describing the average reporter Signal/Noise ratio.
+#'
+#' @description PD column `Average.Reporter.SN` is NA when any tags have missing
+#' values. This function adds an average reporter SN column which ignores missing
+#' values. The assumption is that the intensity values in the `exprs` matrix
+#' are Signal/Noise ratios, as reported by PD by default
+#'
+#' @param obj `MSnSet`. Contains PSMs for TMT quantification
+#' @param sn_col `string`. Name of output column containing the average signal:noise.
+#'
+#' @return Returns an `MSnSet` with the average SN included as a new feature column.
+#' @export
+#' @importFrom MSnbase fData
+update_average_sn <- function(obj,
+                              sn_col='Average.Reporter.SN'){
+
+  MSnbase::fData(obj)[[sn_col]] <- rowMeans(exprs(obj), na.rm=TRUE)
+  obj
+}
+
+
 #' Filter a PSM-level MSnSet to remove low quality PSMs
 #'
 #' @description Filter PSMs from TMT quantification to remove the following:

### 2021-02-01 R/tmt_qc_plots.R

@@ -142,7 +142,7 @@ plot_below_notch_per_prot <- function(notch_per_protein){
   p_notch_per_protein <- notch_per_protein %>%
     group_by(.data$n_below, sample=remove_x(.data$sample)) %>%
     tally() %>%
-    ggplot(aes(sample, n, fill=Hmisc::cut2(
+    ggplot(aes(sample, n, fill=cutr::cutf2(
       .data$n_below, cuts=c(0, 1, 3, 5, 8, 12, 20, 43)))) +
     geom_bar(stat='identity', position='fill') +
     scale_fill_manual(name='# PSMs below notch', values=c('grey', get_cat_palette(6))) +
@@ -188,7 +188,7 @@ plot_fraction_below_notch_per_prot <- function(notch_per_protein){
 #' minimal S:N filtering
 #'
 #' @param obj `MSnSet` containing PSM level TMT intensities
-#' @param sn_column `character` column name for Signal:noise values
+#' @param sn_column `character` column name for signal:noise values
 #' @param bins `numeric` Number of bins to plot
 #'
 #' @return `ggplot` stacked bar plot to show S:N vs # missing values
@@ -204,7 +204,7 @@ plot_missing_SN <- function(obj,
 
   p <- data.frame('n_missing'=n_missing,
                   'sn'=fData(obj)[[sn_column]]) %>%
-    mutate(binned_sn=Hmisc::cut2(.data$sn, g=bins, digits=1)) %>%
+    mutate(binned_sn=cutr::cutf2(.data$sn, g=bins, digits=1)) %>%
     filter(is.finite(.data$sn)) %>%
     group_by(.data$n_missing, .data$binned_sn) %>%
     tally() %>%
@@ -246,7 +246,7 @@ plot_missing_SN_per_sample <- function(obj,
     merge(fData(obj)[,sn_column, drop=FALSE], by.x='PSM_id', by.y='row.names') %>%
     filter(is.finite(.data$Average.Reporter.SN))
 
-  sn_per_sample$binned_sn <- Hmisc::cut2(sn_per_sample[[sn_column]], g=bins, digits=1)
+  sn_per_sample$binned_sn <- cutr::cutf2(sn_per_sample[[sn_column]], g=bins, digits=1)
 
   p <- sn_per_sample %>%
     group_by(.data$sample, .data$binned_sn,

### 2021-02-16 R/psm_tmt_total.R
Document TMT total proteome PSM data
Also:
- provide R script to regenerate .rda file when
  necessary
- delete the .txt file from extdata
- update vignette with new .rda file

@@ -1,0 +1,12 @@
+#' PSM-level PD output for TMT10 plex data
+#'
+#' @description Description.
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @references Insert reference here when published.
+#'
+#' @keywords datasets
+"psm_tmt_total"

### 2021-02-16 R/psm_tmt_phospho.R
Document TMT phospho PSM data
Also:
- provide R script to regenerate .rda file when
  necessary
- delete the .txt file from extdata

@@ -1,4 +1,4 @@
-#' PSM-level PD output for total proteome TMT10-plex data
+#' PSM-level PD output for phospho TMT10-plex data
 #'
 #' @description Description.
 #'
@@ -9,4 +9,4 @@
 #' @references Insert reference here when published.
 #'
 #' @keywords datasets
-"psm_tmt_total"
+"psm_tmt_phospho"

### 2021-03-08 tests/testthat/test-get_ratio.R
Address Tom's comments

@@ -27,5 +27,3 @@ test_that("there are no NAs in the new 'missing' column", {
 
   expect_false(any(is.na(df2$missing)))
 })
-
-#### Sanity checks -------------------------------------------------------------

### 2021-03-08 tests/testthat/test-go.R

@@ -117,22 +117,22 @@ test_that("get_ancestor_go early debug works", {
 
 #### Sanity checks -------------------------------------------------------------
 
-test_that("determine_ancestor_function produces NA is ontology is NA", {
+test_that("determine_ancestor_function produces NA if ontology is NA", {
   result <- determine_ancestor_function(rbp_terms[1], NA)
   expect_identical(result, NA)
 })
 
-test_that("determine_ancestor_function produces NA is ontology is nonsense", {
+test_that("determine_ancestor_function produces NA if ontology is nonsense", {
   result <- determine_ancestor_function(rbp_terms[1], "banana")
   expect_identical(result, NA)
 })
 
-test_that("determine_offspring_function produces NA is ontology is NA", {
+test_that("determine_offspring_function produces NA if ontology is NA", {
   result <- determine_offspring_function(rbp_terms[1], NA)
   expect_identical(result, NA)
 })
 
-test_that("determine_offspring_function produces NA is ontology is nonsense", {
+test_that("determine_offspring_function produces NA if ontology is nonsense", {
   result <- determine_offspring_function(rbp_terms[1], "banana")
   expect_identical(result, NA)
 })

### 2021-03-08 tests/testthat/test-utilities.R

@@ -12,5 +12,3 @@ test_that("remove_dots works", {
   colnames(df) <- remove_dots(colnames(df))
   expect_equal(grep("\\.", colnames(df)), 1)
 })
-
-#### Sanity checks -------------------------------------------------------------

### 2021-03-08 README.Rmd

--- 2021-01-28 README.Rmd
@@
 <!-- badges: start -->
-[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
-[![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR)
+[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
+[![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR?branch=master)
 <!-- badges: end -->

### 2021-03-08 tests/testthat/test-add_site_sequence.R
Clean up tests after merge

@@ -1,17 +1,0 @@
-context('Adding site sequence')
-
-# set up #
-input <- data.frame('protein'=c('L0R819', 'P98196', 'P14618'),
-                    'ptm_position'=c('20', '100', '40'))
-
-
-expected_output <- input
-expected_output$site_seq <- c('VLIPTDNsTPHKEDL', 'PVTSGLPlFFVITVT', NA)
-
-fasta <- system.file("extdata", "reference.fasta", package = "camprotR")
-##########
-# tests #
-test_that("Simple input", {
-  expect_equal(add_site_sequence(input, fasta, master_protein_col='protein'),
-               expected_output)
-})

### 2021-03-08 tests/testthat/test-center-normalise.R

@@ -1,7 +1,0 @@
-context('Center-normalise')
-
-test_that("Center-normalise, no reference", {
-  data('tmt_psm', package='camprotR')
-  expect_equal_to_reference(center_normalise_to_ref(tmt_psm, get_medians(tmt_psm)),
-                            file='tmt_center_normalised.rds')
-})

### 2021-03-08 tests/testthat/test-count_features.R

@@ -1,7 +1,0 @@
-context('Count features per protein')
-
-test_that("Count PSMs", {
-  data('tmt_psm', package='camprotR')
-  expect_equal_to_reference(count_features_per_protein(tmt_psm),
-                            file='tmt_feature_counts.rds')
-})

### 2021-03-08 tests/testthat/test-get_cat_pallete.R

@@ -1,35 +1,0 @@
-context('Categorical colour palette')
-
-test_that("zero colours", {
-  expect_error(get_cat_palette(0))
-})
-
-test_that("13 colours", {
-  expect_error(get_cat_palette(13))
-})
-
-test_that("1 colour", {
-  expect_equal(get_cat_palette(1), "#2271B2")
-})
-
-test_that("7 colours", {
-  expect_equal(get_cat_palette(7),
-               c("#2271B2", "#d55e00", "#359B73", "#e69f00",
-                 "#3DB7E9", "#f0e442", "#F748A5"))
-})
-
-
-test_that("8 colours", {
-  expect_equal(get_cat_palette(8),
-               c("#9F0162", "#009F81", "#FF5AAF", "#00FCCF",
-                 "#8400CD", "#008DF9", "#00C2F9", "#FFB2FD"))
-})
-
-
-test_that("12 colours", {
-  expect_equal(get_cat_palette(12),
-               c("#9F0162", "#009F81", "#FF5AAF", "#00FCCF",
-                 "#8400CD", "#008DF9", "#00C2F9", "#FFB2FD",
-                 "#A40122", "#E20134", "#FF6E3A", "#FFC33B"))
-})
-

### 2021-03-08 tests/testthat/test-match_proteins.R

@@ -1,26 +1,0 @@
-context('Matching protein IDs')
-
-test_that("single protein, matched", {
-  expect_true(camprotR:::match_proteins('prot1', 'prot1'))
-})
-
-test_that("single protein, unmatched", {
-  expect_false(camprotR:::match_proteins('prot1', 'prot2'))
-})
-
-test_that("multiple proteins, matched, same order", {
-  expect_true(camprotR:::match_proteins('prot1; prot2', 'prot1; prot2'))
-})
-
-test_that("multiple proteins, matched, different order", {
-  expect_true(camprotR:::match_proteins('prot1; prot2', 'prot2; prot1'))
-})
-
-test_that("multiple proteins, matched, different sep ", {
-  expect_true(camprotR:::match_proteins('prot1:prot2', 'prot2; prot1',
-                                        sep1=':', sep2='; '))
-})
-
-test_that("multiple proteins, unmatched", {
-  expect_false(camprotR:::match_proteins('prot1; prot2', 'prot2; prot3'))
-})

### 2021-03-08 tests/testthat/test-plot_incorporation.R

@@ -1,25 +1,0 @@
-context('Plot incorporation')
-
-# set up #
-input <- data.frame('incorporation'=c(1, seq(.9,1,.01)))
-output <- c(median(100*input$incorporation),
-            mean(100*input$incorporation))
-
-input_mix <- data.frame('incorporation'=seq(.45,.55,.01),
-                        'corrected_incorporation'=seq(.95,1.05,.01))
-output_mix <- c(median(100*input_mix$incorporation),
-                median(100*input_mix$corrected_incorporation))
-##########
-
-# tests #
-test_that("No mix", {
-  expect_equal(unname(unlist(plot_incorporation(input)$'incorporation_estimates')),
-               output)
-})
-
-# tests #
-test_that("Mix", {
-  expect_equal(unname(unlist(
-    plot_incorporation(input_mix, mix=.5)$'incorporation_estimates')),
-    output_mix)
-})

### 2021-03-08 tests/testthat/test-update_sn.R

@@ -1,8 +1,0 @@
-context('Update average S/N')
-
-test_that("Update average S/N", {
-  data('tmt_psm', package='camprotR')
-  filtered <-  update_average_sn(tmt_psm)
-  expect_equal_to_reference(
-    MSnbase::fData(filtered), file='tmt_psm_f_update_sn.rds')
-})

### 2021-03-08 README.Rmd
Update README

--- 2021-02-01 README.Rmd
@@
 <!-- badges: start -->
-[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/R-CMD-check/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
+[![R-CMD-check](https://github.com/CambridgeCentreForProteomics/camprotR/workflows/check-bioc/badge.svg)](https://github.com/CambridgeCentreForProteomics/camprotR/actions)
 [![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR?branch=master)

### 2021-03-09 R/download_crap.R
Add download_crap() function

@@ -1,0 +1,123 @@
+#' Check the current UniProt release
+#'
+#' @description UniProt releases are published approximately every 8 weeks.
+#' This function checks what the current UniProt release is.
+#'
+#' @return Returns a `character`, the current release number in the format
+#' YYYY_XX where YYYY is the calendar year and XX a 2-digit number that
+#' is incremented for each release of a given year, e.g. 2010_01, 2010_02, etc.
+#'
+#' @examples
+#' # print release number to console
+#' check_uniprot_release()
+#'
+#' # save release number and use in e.g. a file name
+#' rls <- check_uniprot_release()
+#'
+#' paste0("folder/filename_", rls, ".fasta")
+#'
+#' @export
+check_uniprot_release <- function() {
+  # query H. sapiens actin
+  response <- httr::GET(url = "https://www.uniprot.org/uniprot/P60709")
+
+  # basic http error handling
+  httr::stop_for_status(response, "query UniProt")
+
+  # get release
+  response$headers$`x-uniprot-release`
+}
+
+#' Download cRAP/contaminant FASTA files
+#'
+#' @description This function is used to download a specific cRAP/contaminants
+#' sequence database to a FASTA file. The different types of cRAP databases
+#' available through this function currently include:
+#'
+#' - **ccp** = the contaminants database used by the Cambridge Centre for
+#' Proteomics. It is largely based off of The Global Proteome Machine's
+#' cRAP database found [here](https://www.thegpm.org/crap/), with some extra
+#' sequences including commercial proteases added to the end.
+#'
+#' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
+#' @param type `character`, type of cRAP database to download e.g. `"ccp"`
+#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
+#' sequence headers in the FASTA file? Default is `TRUE`
+#' @param overwrite `logical`, if the FASTA file already exists should it be
+#' overwritten? Default is `FALSE`
+#' @param verbose `logical`, should the function send messages to the console?
+#' Default is `TRUE`
+#'
+#' @return Returns a file saved to disk at the specified filepath
+#' @examples
+#' \dontrun{
+#' download_crap("path/to/file/crap_2021_01.fasta", type = "ccp")
+#' }
+#'
[…]

### 2021-03-09 tests/testthat/test-download_crap.R
Test download_crap()

@@ -1,0 +1,27 @@
+context("download_crap")
+
+#### Setup ---------------------------------------------------------------------
+
+download_crap_helper <- function(type) {
+  tmp <- tempfile(fileext = ".fasta")
+  on.exit(file.remove(tmp), add = TRUE, after = TRUE)
+  download_crap(tmp, type = type)
+
+  # read the FASTA
+  crap <- Biostrings::fasta.index(tmp)
+
+  # select columns of interest
+  crap[, c("desc", "seqlength")]
+}
+
+#### Tests ---------------------------------------------------------------------
+test_that("check_uniprot_release works", {
+  expect_true(grepl("[0-9]{4}_[0-9]{2}", check_uniprot_release()))
+})
+
+test_that('download_crap(type = "ccp") works', {
+  expect_equal_to_reference(
+    download_crap_helper(type = "ccp"),
+    "reference/download_crap.rds"
+  )
+})

### 2021-03-09 R/download_crap.R
Add sub_crap() function

@@ -65,14 +65,7 @@ download_crap <- function(file, type = "ccp", add_crap = TRUE,
 
   if (add_crap) {
     crap <- Biostrings::readAAStringSet(filepath = file)
-    old_names <- names(crap)
-    new_names <- mapply(
-      function(on, num) {sub("\\|", paste0("|cRAP", num, "|"), on)},
-      old_names,
-      formatC(seq.int(old_names), width = 3, format = "d", flag = "0"),
-      USE.NAMES = FALSE
-    )
-    names(crap) <- new_names
+    names(crap) <- sub_crap(names(crap))
     Biostrings::writeXStringSet(crap, filepath = file)
   }
 }
@@ -120,4 +113,46 @@ download_ccp_crap <- function(file, overwrite = FALSE, verbose = TRUE) {
     filepath = system.file("extdata", "commercial_reagents.fasta", package = "camprotR")
   )
   Biostrings::writeXStringSet(com_seqs, filepath = file, append = TRUE)
+}
+
+#' Insert cRAP numbers into a character vector
+#'
+#' @description This function takes a character vector where each element is
+#' roughly in the form of a UniProt header e.g. `"sp|XXXXXX|YYYY_YYYY Text goes here"`
+#' and substitutes a cRAP number in place of the first `|` symbol, e.g.
+#' `"sp|cRAP001|XXXXXX|YYYY_YYYY Text goes here"`.
+#'
+#' @param x `character vector`, each element must have two `|` symbols with
+#' some text in between e.g. `|sometext|`.
+#' @param start `numeric`, the number to increment from, default is `1`
+#' @param width `numeric`, how many digits the cRAP number should be, default is `3`
+#'
+#' @return Returns a `character vector` the same length as x.
+#'
+#' @examples
+#' # basic use
+#' sub_crap(c("|sometext|", "|moretext|"))
+#'
+#' # start from a different number
+#' sub_crap(c("|sometext|", "|moretext|"), start = 88)
+#'
+#' # increase number width
+#' sub_crap(c("|sometext|", "|moretext|"), start = 1111, width = 4)
+#'
+#' @export
+sub_crap <- function(x, start = 1, width = 3) {
+  # check input
+  if (!all(grepl("\\|.*\\|", x))) {
+    stop("This function only works when each element of x is a character of the
+         form '|anything|'")
+  }
+
+  output <- mapply(
[…]

### 2021-03-09 tests/testthat/test-download_crap.R

@@ -25,3 +25,9 @@ test_that('download_crap(type = "ccp") works', {
     "reference/download_crap.rds"
   )
 })
+
+test_that("sub_crap works", {
+  expect_equal(sub_crap("|text|"), "|cRAP001|text|")
+  expect_equal(sub_crap("|text|", 77), "|cRAP077|text|")
+  expect_equal(sub_crap("|text|", 111, 4), "|cRAP0111|text|")
+})

### 2021-03-12 R/download_crap.R
Remove download_crap functions

@@ -1,158 +1,0 @@
-#' Check the current UniProt release
-#'
-#' @description UniProt releases are published approximately every 8 weeks.
-#' This function checks what the current UniProt release is.
-#'
-#' @return Returns a `character`, the current release number in the format
-#' YYYY_XX where YYYY is the calendar year and XX a 2-digit number that
-#' is incremented for each release of a given year, e.g. 2010_01, 2010_02, etc.
-#'
-#' @examples
-#' # print release number to console
-#' check_uniprot_release()
-#'
-#' # save release number and use in e.g. a file name
-#' rls <- check_uniprot_release()
-#'
-#' paste0("folder/filename_", rls, ".fasta")
-#'
-#' @export
-check_uniprot_release <- function() {
-  # query H. sapiens actin
-  response <- httr::GET(url = "https://www.uniprot.org/uniprot/P60709")
-
-  # basic http error handling
-  httr::stop_for_status(response, "query UniProt")
-
-  # get release
-  response$headers$`x-uniprot-release`
-}
-
-#' Download cRAP/contaminant FASTA files
-#'
-#' @description This function is used to download a specific cRAP/contaminants
-#' sequence database to a FASTA file. The different types of cRAP databases
-#' available through this function currently include:
-#'
-#' - **ccp** = the contaminants database used by the Cambridge Centre for
-#' Proteomics. It is largely based off of The Global Proteome Machine's
-#' cRAP database found [here](https://www.thegpm.org/crap/), with some extra
-#' sequences including commercial proteases added to the end.
-#'
-#' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
-#' @param type `character`, type of cRAP database to download e.g. `"ccp"`
-#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
-#' sequence headers in the FASTA file? Default is `TRUE`
-#' @param overwrite `logical`, if the FASTA file already exists should it be
-#' overwritten? Default is `FALSE`
-#' @param verbose `logical`, should the function send messages to the console?
-#' Default is `TRUE`
-#'
-#' @return Returns a file saved to disk at the specified filepath
-#' @examples
-#' \dontrun{
-#' download_crap("path/to/file/crap_2021_01.fasta", type = "ccp")
-#' }
[…]

### 2021-03-12 tests/testthat/test-download_crap.R

@@ -1,33 +1,0 @@
-context("download_crap")
-
-#### Setup ---------------------------------------------------------------------
-
-download_crap_helper <- function(type) {
-  tmp <- tempfile(fileext = ".fasta")
-  on.exit(file.remove(tmp), add = TRUE, after = TRUE)
-  download_crap(tmp, type = type)
-
-  # read the FASTA
-  crap <- Biostrings::fasta.index(tmp)
-
-  # select columns of interest
-  crap[, c("desc", "seqlength")]
-}
-
-#### Tests ---------------------------------------------------------------------
-test_that("check_uniprot_release works", {
-  expect_true(grepl("[0-9]{4}_[0-9]{2}", check_uniprot_release()))
-})
-
-test_that('download_crap(type = "ccp") works', {
-  expect_equal_to_reference(
-    download_crap_helper(type = "ccp"),
-    "reference/download_crap.rds"
-  )
-})
-
-test_that("sub_crap works", {
-  expect_equal(sub_crap("|text|"), "|cRAP001|text|")
-  expect_equal(sub_crap("|text|", 77), "|cRAP077|text|")
-  expect_equal(sub_crap("|text|", 111, 4), "|cRAP0111|text|")
-})

### 2021-03-12 R/download_ccp_crap.R
Refactor download_ccp_crap()

@@ -1,0 +1,37 @@
+#' Download CCP cRAP FASTA file
+#'
+#' @description This function is used to download the Cambridge Centre for
+#' Proteomics cRAP FASTA database using sequences from the lastest UniProt release.
+#'
+#' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
+#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
+#' sequence headers in the FASTA file? Default is `TRUE`
+#' @param overwrite `logical`, if the FASTA file already exists should it be
+#' overwritten? Default is `FALSE`
+#' @param verbose `logical`, should the function send messages to the console?
+#' Default is `TRUE`
+#'
+#' @return Returns a FASTA saved to disk at the specified file path.
+#' @examples
+#' \dontrun{
+#' download_ccp_crap("path/to/file/crap_2021_01.fasta")
+#' }
+#'
+#' @export
+download_ccp_crap <- function(file, add_crap = TRUE, overwrite = FALSE, verbose = TRUE) {
+  accessions <- get_ccp_crap()
+
+  make_crap_fasta(accessions = accessions,
+                  file = file,
+                  add_crap = add_crap,
+                  overwrite = overwrite,
+                  verbose = verbose)
+
+  # Add commercial sequences on the end
+  append_crap_fasta(
+    file = system.file("extdata", "commercial_reagents.fasta", package = "camprotR"),
+    crap_file = file,
+    add_crap = add_crap,
+    add_crap_start = 126
+  )
+}

### 2021-03-12 R/make_crap_fasta.R

@@ -1,0 +1,186 @@
+#' Get the UniProt sequences in CCP cRAP
+#'
+#' @description This function take no inputs and simply outputs a vector of the
+#' UniProt accessions for the sequences in the CCP cRAP FASTA.
+#'
+#' @return Returns a `character vector` of UniProt accessions.
+#' @export
+get_ccp_crap <- function() {
+  # load ccp crap and extract accessions
+  input <- Biostrings::readAAStringSet(
+    filepath = system.file("extdata", "cRAP_20190401.fasta", package = "camprotR")
+  ) %>%
+    names()
+
+  accessions <- regmatches(
+    input,
+    gregexpr("(?<=\\|)[A-Z,0-9]{6}(?=\\|)", input, perl = TRUE)
+  ) %>%
+    unlist()
+  accessions[!accessions %in% "000000"]
+}
+
+#' Make a cRAP FASTA using UniProt accessions
+#'
+#' @description Given a vector of UniProt accessions, this function will:
+#' 1. Download the sequences
+#' 2. Print the current UniProt release (you should put this in the FASTA file name)
+#' 3. (Optional) add cRAP numbers to the FASTA headers for each sequence
+#' 4. Save the sequences in a FASTA file
+#'
+#' @param accessions `character vector`, the UniProt accessions to use
+#' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
+#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
+#' sequence headers in the FASTA file? Default is `TRUE`
+#' @param overwrite `logical`, if the FASTA file already exists should it be
+#' overwritten? Default is `FALSE`
+#' @param verbose `logical`, should the function send messages to the console?
+#' Default is `TRUE`
+#'
+#' @return Returns a FASTA file saved to disk at the specified file path.
+#' @examples
+#' # specify some UniProt accessions
+#' crap <- get_ccp_crap()
+#'
+#' \dontrun{
+#' make_crap_fasta(crap, "crap_2021-01.fasta")
+#' }
+#'
+#' @export
+make_crap_fasta <- function(accessions, file, add_crap = TRUE, overwrite = FALSE, verbose = TRUE) {
+  # define payload used to query uniprot
+  payload <- list(
+    query = paste(accessions, collapse = " "),
+    from = "ACC+ID",
+    to = "ACC",
+    format = "fasta"
+  )
+
+  # query uniprot and save FASTA to disk
+  response <- httr::GET(
[…]

### 2021-03-12 tests/testthat/test-download_ccp_crap.R

@@ -1,0 +1,33 @@
+context("download_ccp_crap")
+
+#### Setup ---------------------------------------------------------------------
+
+download_ccp_crap_helper <- function() {
+  tmp <- tempfile(fileext = ".fasta")
+  on.exit(file.remove(tmp), add = TRUE, after = TRUE)
+  download_ccp_crap(tmp)
+
+  # read the FASTA
+  crap <- Biostrings::fasta.index(tmp)
+
+  # select columns of interest
+  crap[, c("desc", "seqlength")]
+}
+
+#### Tests ---------------------------------------------------------------------
+test_that("check_uniprot_release works", {
+  expect_true(grepl("[0-9]{4}_[0-9]{2}", check_uniprot_release()))
+})
+
+test_that('download_ccp_crap works', {
+  expect_equal_to_reference(
+    download_ccp_crap_helper(),
+    "reference/download_ccp_crap.rds"
+  )
+})
+
+test_that("sub_crap works", {
+  expect_equal(sub_crap("|text|"), "|cRAP001|text|")
+  expect_equal(sub_crap("|text|", 77), "|cRAP077|text|")
+  expect_equal(sub_crap("|text|", 111, 4), "|cRAP0111|text|")
+})

### 2021-03-12 R/make_crap_fasta.R
Fix append_crap_fasta docs

@@ -86,6 +86,8 @@ make_crap_fasta <- function(accessions, file, add_crap = TRUE, overwrite = FALSE
 #' @param crap_file `character`, file path of existing cRAP FASTA to append to
 #' @param add_crap add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
 #' sequence headers in the FASTA to append? Default is `TRUE`
+#' @param add_crap_start `numeric`, what number should the cRAP00x start at?
+#' Default is 1.
 #'
 #' @return Returns the existing cRAP FASTA file with some more sequences added
 #' to the end.

### 2021-03-17 R/append_fasta.R
Rename make_fasta()

@@ -1,0 +1,37 @@
+#' Append sequences to end of cRAP FASTA
+#'
+#' @description This function is used to add sequences from a FASTA file onto
+#' the end of an existing cRAP FASTA file.
+#'
+#' @param file `character`, file path of FASTA to append
+#' @param crap_file `character`, file path of existing cRAP FASTA to append to
+#' @param add_crap add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
+#' sequence headers in the FASTA to append? Default is `TRUE`
+#' @param add_crap_start `numeric`, what number should the cRAP00x start at?
+#' Default is 1.
+#'
+#' @return Returns the existing cRAP FASTA file with some more sequences added
+#' to the end.
+#' @examples
+#' # Add some commerical protease sequences onto the end of CCP cRAP FASTA
+#' \dontrun{
+#' append_crap_fasta(
+#'   file = "commercial-proteases.fasta",
+#'   crap_file = "ccp_crap_2021-01.fasta",
+#'   add_crap = TRUE
+#' )
+#' }
+#'
+#' @export
+append_crap_fasta <- function(file, crap_file, add_crap = TRUE, add_crap_start = 1) {
+  # read in file to append
+  to_append <- Biostrings::readAAStringSet(file)
+
+  # add cRAP to headers if specified
+  if (add_crap) {
+    names(to_append) <- sub_crap(names(to_append), start = add_crap_start)
+  }
+
+  # append sequences
+  Biostrings::writeXStringSet(to_append, filepath = crap_file, append = TRUE)
+}

### 2021-03-17 R/make_fasta.R

@@ -20,7 +20,7 @@ get_ccp_crap <- function() {
   accessions[!accessions %in% "000000"]
 }
 
-#' Make a cRAP FASTA using UniProt accessions
+#' Make a FASTA using UniProt accessions
 #'
 #' @description Given a vector of UniProt accessions, this function will:
 #' 1. Download the sequences
@@ -30,8 +30,9 @@ get_ccp_crap <- function() {
 #'
 #' @param accessions `character vector`, the UniProt accessions to use
 #' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
-#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
-#' sequence headers in the FASTA file? Default is `TRUE`
+#' @param is_crap `logical`, Is the output going to be a cRAP database? If `TRUE`
+#' cRAP001, cRAP002, etc. is appended to the sequence headers in the FASTA file.
+#' Default is `FALSE`
 #' @param overwrite `logical`, if the FASTA file already exists should it be
 #' overwritten? Default is `FALSE`
 #' @param verbose `logical`, should the function send messages to the console?
@@ -43,11 +44,11 @@ get_ccp_crap <- function() {
 #' crap <- get_ccp_crap()
 #'
 #' \dontrun{
-#' make_crap_fasta(crap, "crap_2021-01.fasta")
+#' make_fasta(crap, "2021-01_cRAP.fasta")
 #' }
 #'
 #' @export
-make_crap_fasta <- function(accessions, file, add_crap = TRUE, overwrite = FALSE, verbose = TRUE) {
+make_fasta <- function(accessions, file, is_crap = FALSE, overwrite = FALSE, verbose = TRUE) {
   # define payload used to query uniprot
   payload <- list(
     query = paste(accessions, collapse = " "),
@@ -70,49 +71,11 @@ make_crap_fasta <- function(accessions, file, add_crap = TRUE, overwrite = FALSE
   if (verbose) message(paste("Downloading from UniProtKB release:",
                              response$headers$`x-uniprot-release`))
 
-  if (add_crap) {
+  if (is_crap) {
     crap <- Biostrings::readAAStringSet(filepath = file)
     names(crap) <- sub_crap(names(crap))
     Biostrings::writeXStringSet(crap, filepath = file)
   }
-}
-
-#' Append sequences to end of cRAP FASTA
-#'
-#' @description This function is used to add sequences from a FASTA file onto
[…]

### 2021-03-17 R/append_fasta.R
Rename append_fasta()

@@ -1,37 +1,42 @@
-#' Append sequences to end of cRAP FASTA
+#' Append sequences to end of a FASTA
 #'
-#' @description This function is used to add sequences from a FASTA file onto
-#' the end of an existing cRAP FASTA file.
+#' @description This function is used to add sequences from a FASTA file (file1)
+#' onto the end of another FASTA file (file2).
 #'
-#' @param file `character`, file path of FASTA to append
-#' @param crap_file `character`, file path of existing cRAP FASTA to append to
-#' @param add_crap add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
-#' sequence headers in the FASTA to append? Default is `TRUE`
-#' @param add_crap_start `numeric`, what number should the cRAP00x start at?
+#' If file2 is a cRAP database, then you can optionally add cRAP numbers to the
+#' headers of file1, starting at the desired number e.g. cRAP127.
+#'
+#' @param file1 `character`, file path of FASTA to append
+#' @param file2 `character`, file path of FASTA to append to
+#' @param is_crap `logical`, should cRAP numbers e.g. cRAP001, cRAP002, etc.
+#' be added to sequence headers of file1? Default is `FALSE`
+#' @param crap_start `numeric`, what number should the cRAP00x start at?
 #' Default is 1.
 #'
-#' @return Returns the existing cRAP FASTA file with some more sequences added
+#' @return Overwrites FASTA file2 with some more sequences added
 #' to the end.
+#'
 #' @examples
-#' # Add some commerical protease sequences onto the end of CCP cRAP FASTA
+#' # Add some commercial protease sequences onto the end of CCP cRAP FASTA
 #' \dontrun{
-#' append_crap_fasta(
-#'   file = "commercial-proteases.fasta",
-#'   crap_file = "ccp_crap_2021-01.fasta",
-#'   add_crap = TRUE
+#' append_fasta(
+#'   file1 = "commercial-proteases.fasta",
+#'   file2 = "2021-01_CCP_cRAP.fasta",
+#'   is_crap = TRUE,
+#'   crap_start = 128
 #' )
 #' }
 #'
 #' @export
-append_crap_fasta <- function(file, crap_file, add_crap = TRUE, add_crap_start = 1) {
+append_fasta <- function(file1, file2, is_crap = FALSE, crap_start = 1) {
   # read in file to append
-  to_append <- Biostrings::readAAStringSet(file)
[…]

### 2021-03-17 R/download_ccp_crap.R
Update download_ccp_crap()

@@ -4,7 +4,7 @@
 #' Proteomics cRAP FASTA database using sequences from the lastest UniProt release.
 #'
 #' @param file `character`, filepath to save the fasta to e.g. `"crap.fasta"`
-#' @param add_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
+#' @param is_crap `logical`, should cRAP001, cRAP002, etc. be appended to the
 #' sequence headers in the FASTA file? Default is `TRUE`
 #' @param overwrite `logical`, if the FASTA file already exists should it be
 #' overwritten? Default is `FALSE`
@@ -14,24 +14,24 @@
 #' @return Returns a FASTA saved to disk at the specified file path.
 #' @examples
 #' \dontrun{
-#' download_ccp_crap("path/to/file/crap_2021_01.fasta")
+#' download_ccp_crap("path/to/file/2021-01_CCP_cRAP.fasta")
 #' }
 #'
 #' @export
-download_ccp_crap <- function(file, add_crap = TRUE, overwrite = FALSE, verbose = TRUE) {
+download_ccp_crap <- function(file, is_crap = TRUE, overwrite = FALSE, verbose = TRUE) {
   accessions <- get_ccp_crap()
 
-  make_crap_fasta(accessions = accessions,
+  make_fasta(accessions = accessions,
                   file = file,
-                  add_crap = add_crap,
+                  is_crap = is_crap,
                   overwrite = overwrite,
                   verbose = verbose)
 
   # Add commercial sequences on the end
-  append_crap_fasta(
-    file = system.file("extdata", "commercial_reagents.fasta", package = "camprotR"),
-    crap_file = file,
-    add_crap = add_crap,
-    add_crap_start = 126
+  append_fasta(
+    file1 = system.file("extdata", "commercial_reagents.fasta", package = "camprotR"),
+    file2 = file,
+    is_crap = is_crap,
+    crap_start = 126
   )
 }

### 2021-03-19 README.Rmd
Update README and crap.Rmd

@@
 [![codecov](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR/branch/master/graph/badge.svg)](https://codecov.io/gh/CambridgeCentreForProteomics/camprotR?branch=master)
+[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg)](https://opensource.org/licenses/MIT)
 <!-- badges: end -->
+
+The `camprotR` package is an internal package written and used by the 
+[Cambridge Centre for Proteomics](https://proteomics.bio.cam.ac.uk) to 
+facilitate our proteomic analyses. It is opinionated by design and most 
+functions assume the data has been processed by Proteome Discoverer.
+
+## Install
+
+```{r, eval=FALSE}
+remotes::install_github("CambridgeCentreForProteomics/camprotR", build_vignettes = TRUE)
+```
+
+## How to use
+
+Several HTML vignettes are installed with this package which go through how to
+use different aspects of the package. You can see a list of available vignettes
+with:
+
+```{r, eval=FALSE}
+browseVignettes("camprotR")
+```

### 2021-09-14 R/filter_x.R
Remove magrittr from examples

@@ -53,16 +53,14 @@ subset_na <- function(data, op = c("==", "<=", ">=", "!="), regex, value) {
 #'
 #' @return Returns a filtered object of the same class as `data`.
 #' @examples
-#' library(magrittr)
-#'
 #' # set a seed for reproducibility
 #' set.seed(123)
 #'
 #' # make a data.frame with fake protein/peptide abundance data
-#' df <- cbind(replicate(3, runif(7, 13, 24)),
-#'             replicate(3, runif(7, 24, 30))) %>%
-#'  as.data.frame() %>%
-#'  `colnames<-`(c(paste0("ctr", 1:3), paste0("trt", 1:3)))
+#' df <- as.data.frame(cbind(replicate(3, runif(7, 13, 24)),
+#'                           replicate(3, runif(7, 24, 30))))
+#'
+#' colnames(df) <- c(paste0("ctr", 1:3), paste0("trt", 1:3))
 #'
 #' # add in some missing values
 #' mapply(function(i, j) {
@@ -148,16 +146,14 @@ subset_zero <- function(data, op = c("==", "<=", ">=", "!="), regex, value) {
 #'
 #' @return Returns a filtered object of the same class as `data`.
 #' @examples
-#' library(magrittr)
-#'
 #' # set a seed for reproducibility
 #' set.seed(123)
 #'
 #' # make a data.frame with fake protein/peptide abundance data
-#' df <- cbind(replicate(3, runif(7, 13, 24)),
-#'             replicate(3, runif(7, 24, 30))) %>%
-#'  as.data.frame() %>%
-#'  `colnames<-`(c(paste0("ctr", 1:3), paste0("trt", 1:3)))
+#' df <- as.data.frame(cbind(replicate(3, runif(7, 13, 24)),
+#'                           replicate(3, runif(7, 24, 30))))
+#'
+#' colnames(df) <- c(paste0("ctr", 1:3), paste0("trt", 1:3))
 #'
 #' # add in some 0 values
 #' mapply(function(i, j) {
@@ -242,16 +238,14 @@ subset_val <- function(data, op = c("==", "<=", ">=", "!="), regex, value) {
 #'
 #' @return Returns a filtered object of the same class as `data`.
 #' @examples
-#' library(magrittr)
-#'
 #' # set a seed for reproducibility
 #' set.seed(123)
 #'
 #' # make a data.frame with fake protein/peptide abundance data
[…]

### 2021-09-15 R/go.R
Fix message type in get_enriched_go()

@@ -271,7 +271,7 @@ get_enriched_go <- function(pwf, gene2cat = NULL, ...,
     out <- goseq::goseq(pwf = pwf, gene2cat = gene2cat, ...)
   } else {
     message(sprintf("Number of DE genes input: %i", sum(pwf$DEgenes)))
-    message('gene2cat not provided. Defaulting to genome = "hg" and id = "ensGene"')
+    message('gene2cat not provided. Defaulting to genome = "hg19" and id = "ensGene"')
     out <- goseq::goseq(pwf, genome = "hg19", id = "ensGene", ...)
   }
 

### 2021-11-03 tests/testthat/test-estimate_incorporation.R
Test estimate_incorporation()

@@ -1,0 +1,34 @@
+test_that("estimate_incorporation() works", {
+  # estimate incorporation and output to incorporation folder
+  out <- estimate_incorporation(
+    psm_input = psm_silac_p4,
+    peptide_input = pep_silac_p4,
+    crap_fasta = system.file("extdata/cRAP_20190401.fasta.gz", package = "camprotR"),
+    mix = 1
+  )
+
+  # check plot outputs
+  vdiffr::expect_doppelganger(
+    "estimate-incorporation-HL-correlation",
+    out$HL_correlation
+  )
+
+  vdiffr::expect_doppelganger(
+    "estimate-incorporation-peptide",
+    out$peptide_incorporation
+  )
+
+  vdiffr::expect_doppelganger(
+    "estimate-incorporation-protein",
+    out$protein_incorporation
+  )
+
+  # check table output
+  withr::with_tempfile("tf", {
+    # save output to tempfile
+    write.table(out$incorporation_table, file = tf,
+                sep = "\t", row.names = FALSE, col.names = TRUE)
+
+    expect_snapshot_file(tf, "estimate-incorporation-table")
+  })
+})

### 2021-11-03 R/silac_psm_seq_int.R
Fix failing tests (hopefully)

@@ -21,7 +21,7 @@ silac_psm_seq_int <- function(
   interference_col='Isolation.Interference.in.Percent'){
 
   # check that input files have the necessary columns
-  required_cols <- c("Sequence", "Modifications", "Isolation.Interference.in.Percent",
+  required_cols <- c(sequence_col, mod_col, interference_col,
                      "Quan.Channel", "Precursor.Abundance")
 
   if (!all(required_cols %in% colnames(obj))) {

### 2021-11-03 tests/testthat/test-extract_psm_info.R

@@ -1,28 +1,0 @@
-snap_psm_seq_int <- function(infile, sequence_col) {
-  # make a tempfile to compare against snapshot file
-  path <- tempfile(tmpdir = test_path("testdata"), fileext = ".txt")
-
-  # read in data to for function to use
-  df <- read.table(file = infile, header = TRUE, sep = "\t")
-
-  # run function to test and capture output
-  out <- silac_psm_seq_int(df, sequence_col = sequence_col)
-
-  # save output to tempfile
-  write.table(out, file = path,
-              sep = "\t", row.names = FALSE, col.names = TRUE)
-
-  # return path of tempfile
-  return(path)
-}
-
-test_that("silac_psm_seq_int() works", {
-  # compare tempfile to snapshot file
-  expect_snapshot_file(
-    snap_psm_seq_int(
-      infile = test_path("testdata/small_psm_silac_p4.txt"),
-      sequence_col = "Annotated.Sequence"
-    ),
-    "silac_psm_seq_int.txt"
-  )
-})

### 2021-11-03 tests/testthat/test-silac_psm_seq_int.R

@@ -1,17 +1,28 @@
-context('extract_psm_info')
+snap_psm_seq_int <- function(infile, sequence_col) {
+  # make a tempfile to compare against snapshot file
+  path <- tempfile(tmpdir = test_path("testdata"), fileext = ".txt")
 
-#### Setup ---------------------------------------------------------------------
+  # read in data to for function to use
+  df <- read.table(file = infile, header = TRUE, sep = "\t")
 
-small_psm_silac <- read.delim(
-  system.file("testdata", "small_psm_silac.txt", package = "camprotR")
-)
+  # run function to test and capture output
+  out <- silac_psm_seq_int(df, sequence_col = sequence_col)
 
-#### Tests ---------------------------------------------------------------------
-test_that("silac_psm_seq_int works", {
-  expect_equal_to_reference(
-    silac_psm_seq_int(small_psm_silac, sequence_col='Annotated.Sequence'),
-    "reference/silac_psm_seq_int.rds"
+  # save output to tempfile
+  write.table(out, file = path,
+              sep = "\t", row.names = FALSE, col.names = TRUE)
+
+  # return path of tempfile
+  return(path)
+}
+
+test_that("silac_psm_seq_int() works", {
+  # compare tempfile to snapshot file
+  expect_snapshot_file(
+    snap_psm_seq_int(
+      infile = test_path("testdata/small_psm_silac_p4.txt"),
+      sequence_col = "Annotated.Sequence"
+    ),
+    "silac_psm_seq_int.txt"
   )
 })
-
-#### Sanity checks -------------------------------------------------------------

### 2022-01-31 R/psm_oops_2.R
adds data for SILAC vignette and starts vignette

@@ -1,0 +1,12 @@
+#' PSM PD output for SILAC labelled U-2 OS cells
+#'
+#' @description OOPS CL vs NC, H=CL, L=NC.
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @references Insert reference here when published.
+#'
+#' @keywords datasets
+"psm_oops_2"

### 2022-02-24 R/dep_results.R
Ts add vignettes (#37)
* avoids error in remove_redundant_go when GO term has no ontology

* Fix message type in get_enriched_go()

* Add dataset from DEP package

Results of a differential enrichment analysis on
LFQ data which is provided in the DEP package.

Will be used for testing GO functions amongst
other things.

* Check input data type

get_enriched_go()

* minor updates to TMT vignette

* adds data for SILAC vignette and starts vignette

* adds futher steps to SILAC vignette

* Updates TMT vignette to clarify when notch section can be skipped

* Contiunes SILAC vignette

* Make silac_

@@ -1,0 +1,12 @@
+#' Results table from DEP package
+#'
+#' @description Description.
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @references Insert reference here.
+#'
+#' @keywords datasets
+"dep_results"

### 2022-02-24 R/go.R

@@ -271,7 +271,7 @@ get_enriched_go <- function(pwf, gene2cat = NULL, ...,
     out <- goseq::goseq(pwf = pwf, gene2cat = gene2cat, ...)
   } else {
     message(sprintf("Number of DE genes input: %i", sum(pwf$DEgenes)))
-    message('gene2cat not provided. Defaulting to genome = "hg" and id = "ensGene"')
+    message('gene2cat not provided. Defaulting to genome = "hg19" and id = "ensGene"')
     out <- goseq::goseq(pwf, genome = "hg19", id = "ensGene", ...)
   }
 
@@ -323,6 +323,14 @@ get_enriched_go <- function(pwf, gene2cat = NULL, ...,
 #'
 #' @export
 estimate_go_overrep <- function(obj, pwf, gene2cat) {
+  # if gene2cat is a list, convert to data.frame of correct format
+  if (is.list(gene2cat)) {
+    gene2cat <- gene2cat %>%
+      tibble::enframe(name = "id", value = "go_terms") %>%
+      tidyr::unnest(cols = c("id", "go_terms")) %>%
+      as.data.frame()
+  }
+
   n_de_genes <- sum(pwf$DEgenes)
   n_genes <- length(pwf$DEgenes)
 
@@ -377,6 +385,22 @@ remove_redundant_go <- function(obj) {
     columns = c("ONTOLOGY")
   )
   ontologies <- setNames(ontologies$ONTOLOGY, ontologies$GOID)
+
+  if (any(is.na(ontologies))) {
+    # get names of GO terms that failed to be matched
+    bad.terms <- names(ontologies[is.na(ontologies) == TRUE])
+
+    warning(
+      "Warning: the following GO terms failed to match to a primary ontology ",
+      "in GO.db and were removed: ",
+      paste(bad.terms, collapse = ", ")
+    )
+    # remove NA ontologies
+    ontologies <- ontologies[!is.na(ontologies)]
+
+    # remove corresponding GO ids
+    all_observed_go <- all_observed_go[!all_observed_go %in% bad.terms]
+  }
 
   # get ancestor and offspring GO terms of parent GO terms
   offspring <- get_all_mappings(all_observed_go, ontologies, verbose = FALSE, direction = "offspring")

### 2022-02-24 R/pep_oops_1.R

@@ -1,0 +1,12 @@
+#' PeptideGroups PD output for SILAC labelled U-2 OS cells
+#'
+#' @description OOPS CL vs NC, H=CL, L=NC.
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @references Insert reference here when published.
+#'
+#' @keywords datasets
+"pep_oops_1"

### 2022-02-24 R/pep_oops_4.R

@@ -1,0 +1,12 @@
+#' PeptideGroups PD output for SILAC labelled U-2 OS cells
+#'
+#' @description OOPS CL vs NC, H=NC, L=CL.
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @references Insert reference here when published.
+#'
+#' @keywords datasets
+"pep_oops_4"

### 2022-02-24 data-raw/silac_comparison.R

@@ -1,0 +1,42 @@
+library(dplyr)
+# files from https://github.com/CambridgeCentreForProteomics/infSILAC/tree/master/raw/exp_2
+silac_pep_infiles <- Sys.glob(here::here('data-raw/OOPS*_PeptideGroups.txt'))
+silac_psm_infiles <- Sys.glob(here::here('data-raw/OOPS*_PSMs.txt'))
+
+pep_data <- lapply(silac_pep_infiles, read.delim)
+psm_data <- lapply(silac_psm_infiles, read.delim)
+
+# Sample 100 proteins to keep
+
+set.seed(0)
+
+proteins <- lapply(pep_data, function(x) x$Master.Protein.Accessions) %>%
+  Reduce(f='intersect') %>%
+  unique()
+
+keep_proteins <- sample(proteins[!grepl(';', proteins)], 100)
+
+filter_inf <- function(x){
+  x %>%
+    filter((grepl('cRAP', Master.Protein.Accessions) |
+              Master.Protein.Accessions %in% keep_proteins))
+}
+
+psm_oops_1 <- psm_data[[1]] %>% filter_inf()
+psm_oops_2 <- psm_data[[2]] %>% filter_inf()
+psm_oops_3 <- psm_data[[3]] %>% filter_inf()
+psm_oops_4 <- psm_data[[4]] %>% filter_inf()
+pep_oops_1 <- pep_data[[1]] %>% filter_inf()
+pep_oops_2 <- pep_data[[2]] %>% filter_inf()
+pep_oops_3 <- pep_data[[3]] %>% filter_inf()
+pep_oops_4 <- pep_data[[4]] %>% filter_inf()
+
+usethis::use_data(psm_oops_1, overwrite=TRUE)
+usethis::use_data(psm_oops_2, overwrite=TRUE)
+usethis::use_data(psm_oops_3, overwrite=TRUE)
+usethis::use_data(psm_oops_4, overwrite=TRUE)
+usethis::use_data(pep_oops_1, overwrite=TRUE)
+usethis::use_data(pep_oops_2, overwrite=TRUE)
+usethis::use_data(pep_oops_3, overwrite=TRUE)
+usethis::use_data(pep_oops_4, overwrite=TRUE)
+

### 2022-02-24 data-raw/silac_p4.R

@@ -1,0 +1,34 @@
+library(dplyr)
+
+# Read in SILAC passage 4 peptide data
+# 50:50 mix of light:heavy cells (R0K0:R10K8)
+pepg <- read.delim(
+  here::here("data-raw/Molm_13_P4_PeptideGroups.txt")
+)
+
+# Read in corresponding PSM data
+silac_p4 <- read.delim(
+  here::here("data-raw/Molm_13_P4_PSMs.txt")
+)
+
+# Remove extraneous periods from colnames
+colnames(pepg) <- camprotR::remove_dots(colnames(pepg))
+colnames(silac_p4) <- camprotR::remove_dots(colnames(silac_p4))
+
+# Set seed for reproducible sampling
+set.seed(2021)
+
+# Get a random sample of 100 Master proteins
+prot_sample <- sample(unique(pepg$Master.Protein.Accessions), 100)
+
+# Get all peptides for this random sample
+pep_silac_p4 <- filter(pepg, Master.Protein.Accessions %in% prot_sample)
+
+# Get all PSMs for this random sample
+psm_silac_p4 <- filter(silac_p4, Master.Protein.Accessions %in% prot_sample)
+
+# Output peptide .rda file
+usethis::use_data(pep_silac_p4, overwrite = TRUE)
+
+# Output psm .rda file
+usethis::use_data(psm_silac_p4, overwrite = TRUE)

### 2022-03-08 R/lfq_oops_rnase.R
adds LFQ vignette

@@ -1,0 +1,13 @@
+#' PeptideGroups PD output for LFQ of RNase +/- OOPS experiment
+#'
+#' @description OOPS CL vs NC
+#' F17-20 = RNase(-) reps 1-4
+#' F21-24 = RNase(+) reps 1-4
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @keywords datasets
+"lfq_oops_rnase"
+

### 2022-03-08 data-raw/lfq_rbpmap.R

@@ -1,0 +1,15 @@
+# Load libraries
+library(dplyr)
+
+# All files from https://github.com/CambridgeCentreForProteomics/RBPMap_RNase/tree/master/pilot_3/raw
+# Read in PSM data
+'./data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt'
+lfq_oops_rnase <- read.delim(
+  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt")
+)
+
+# Adding an artifical protein accessions column as this is needed for camprotR::parse_features
+lfq_oops_rnase$Protein.Accessions <- lfq_oops_rnase$Master.Protein.Accessions
+
+# Output .rda file
+usethis::use_data(lfq_oops_rnase)

### 2022-03-08 R/glycoproteins.R
finalises LFQ vignette to protein inference

@@ -1,0 +1,11 @@
+#' Glycoproteoins
+#'
+#' @description data.fram with glycoproteins for use in LFQ vignette
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#'
+#' @keywords datasets
+"glycoproteins"

### 2022-03-09 R/normalise.R
finalises first draft LFQ vignette

@@ -25,15 +25,24 @@ get_medians <- function(obj){
 #'
 #' @param obj `MSnSet`. Contains PSMs.
 #' @param medians `vector, numeric`. Sample medians from reference dataset
-#'
+#' @param center_to_zero `logical`. Centre the data range on zero.
+#' If FALSE, normalisation retains original data range.
+#' @param on_log_scale `logical`. Input data is log-transformed
 #' @return Returns an `MSnSet` with the expression matrix column center-median
 #' normalised
 #'
 #' @export
-center_normalise_to_ref <- function(obj, medians){
+center_normalise_to_ref <- function(obj, medians,
+                                    center_to_zero=FALSE,
+                                    on_log_scale=FALSE){
 
-  medians <- medians/mean(medians)
-  exprs(obj) <- t(t(exprs(obj))/medians)
+  if(!center_to_zero) medians <- medians/mean(medians)
+
+  if(on_log_scale){
+    exprs(obj) <- t(t(exprs(obj)) - medians)
+  } else{
+    exprs(obj) <- t(t(exprs(obj)) / medians)
+  }
 
   return(obj)
 }

### 2022-04-06 R/go.R
Fix `estimate_go_overrep()` input check

@@ -324,7 +324,7 @@ get_enriched_go <- function(pwf, gene2cat = NULL, ...,
 #' @export
 estimate_go_overrep <- function(obj, pwf, gene2cat) {
   # if gene2cat is a list, convert to data.frame of correct format
-  if (is.list(gene2cat)) {
+  if (is.list(gene2cat) & !is.data.frame(gene2cat)) {
     gene2cat <- gene2cat %>%
       tibble::enframe(name = "id", value = "go_terms") %>%
       tidyr::unnest(cols = c("id", "go_terms")) %>%

### 2022-04-06 R/go.R
Refactor and document `plot_go()`

@@ -456,45 +456,75 @@ remove_redundant_go <- function(obj) {
 #' @description This function plots a set of GO terms of interest.
 #' be run after \code{\link{get_enriched_go}} and \code{\link{estimate_go_overrep}}.
 #' To avoid plotting too many terms, you may wish to use
-#' \code{\link{remove_redundant_go}} first too.
+#' \code{\link{remove_redundant_go}} first too. A warning is shown if you try
+#' and plot more than 100 GO terms.
 #'
 #' @param obj `data.frame` containing `goseq` results as generated by
 #' \code{\link{get_enriched_go}} then \code{\link[goseq]{estimate_go_overrep}}.
-#' @param term_col `character` column name for GO term description
-#' @param ontology_col `character` column name for GO term ontology
-#' @param annot_n `logical` Include the number of features per term in the plot
+#' See below for an example.
+#' @param term_col `character` column name for GO term description.
+#' @param ontology_col `character` column name for GO term ontology.
+#' @param annotate_n `logical` Include the number of features per term
+#' (i.e. numDEInCat column) in the plot? (Default is `TRUE`)
 #'
-#' @return Returns `ggplot`
+#' @return Returns a `ggplot` object.
 #'
 #' @export
 plot_go <- function(obj,
-                    term_col='term_short',
-                    ontology_col='ontology',
-                    annot_n=TRUE){
+                    term_col = "term_short",
+                    ontology_col = "ontology",
+                    annotate_n = TRUE) {
 
-  .to_plot <- obj %>%
+
+
+  # throw an error if peptide input does not contain the required columns
+  req_cols <- c(term_col, ontology_col, "over_represented_adj_pval",
+                "adj_overrep", "numDEInCat")
+
+  if (!all(req_cols %in% colnames(obj))) {
+    stop(
+      paste("The input data.frame is missing the following required columns:",
+            req_cols[!req_cols %in% colnames(obj)])
+    )
+  }
+
+  # throw a warning if trying to plot more than 100 GO terms
+  if (nrow(obj) > 100) warning("Trying to plot more than 100 GO terms is not advisable.")
+
+  # print message if term_col contains non-unique values
+  if (any(duplicated(obj[, term_col]))) {
[…]

### 2022-04-07 R/go.R
Update docs for GO functions

@@ -63,17 +63,18 @@ determine_offspring_function <- function(term, ontology) {
 
 #' Get all mappings for GO terms
 #'
-#' For a set of GO terms, obtain all of the ancestor or offspring terms.
+#' For a vector of GO terms, obtain all of the ancestor or offspring terms.
 #'
-#' @param go_ids `character vector`. The GO.IDs to use
-#' @param ontologies `named character vector`. Names = GO.IDs and values =
-#' Ontologies e.g. BP, CC, MF.
+#' @param go_ids `character vector`. GO terms to use in the format `GO:1234567`.
+#' @param ontologies `named character vector`. Names = `go_ids` and values =
+#' ontologies e.g. `BP`, `CC`, or `MF`.
 #' @param verbose `logical`.
-#' @param direction `string` Either `"ancestor"` or
-#' `"offspring"`.
+#' @param direction `string` Either `"ancestor"` or `"offspring"`.
 #'
-#' @return Returns a `named list` of `character vectors`. Names = GO.IDs and
-#' values = all ancestor GO.IDs.
+#' @return Returns a `named list` of `character vectors`. Names == GO terms and
+#' values == vectors containing all ancestor GO terms for the particular input
+#' GO term.
+#'
 #' @importFrom purrr map2
 #' @keywords internal
 #' @export
@@ -122,15 +123,17 @@ get_all_mappings <- function(go_ids, ontologies, verbose = TRUE, direction = "an
 #' a single column. Output is a new data.frame with all of the GO terms for
 #' that protein (annotated and ancestor).
 #'
-#' @param go_df `data.frame` for a single protein with a column ==
-#' `"GO.ID"`.
+#' @param go_df `data.frame` for a single protein with a single column where
+#' each row is a single GO term.
 #' @param go_col `variable`. Name of column from the data.frame that
 #' contains the GO terms.
-#' @param go2Ancestor `named list`. Returned by get_all_mappings.
-#' Names == GO.IDs and values == all ancestor GO.IDs.
+#' @param go2Ancestor `named list`. Returned by \code{\link{get_all_mappings}}.
+#' Names == GO terms and values == vectors containing all ancestor GO terms
+#' for the particular input GO term.
 #'
 #' @return Returns a `data.frame` containing all ancestor GO terms for a
 #' single protein.
+#'
 #' @keywords internal
 #' @export
[…]

### 2022-04-07 tests/testthat/test-go.R
Add GO function tests

@@ -1,0 +1,177 @@
+test_that("expand_terms() works", {
+  # Imagine some made-up protein X which has the following GO terms annotated
+  # mRNA cap binding, RNA binding, cytoplasmic region, innate immune response
+  go_df <- data.frame(
+    GO.ID =  c("GO:0098808", "GO:0003723", "GO:0099568", "GO:0045087"),
+    GO.ONT = c("MF", "MF", "CC", "BP")
+  )
+
+  # need to run `get_all_mappings()` first
+  expanded_go <- get_all_mappings(
+    go_ids = go_df$GO.ID,
+    ontologies = go_df$GO.ONT,
+    verbose = TRUE,
+    direction = "ancestor"
+  )
+
+  # construct input for `get_all_mappings()`
+  go_2_ancestor <- go_df$GO.ID
+  names(go_2_ancestor) <- go_df$GO.ONT
+
+  # run `expand_terms()` to test and capture output
+  out <- expand_terms(
+    go_df = go_df,
+    go_col = "GO.ID",
+    go2Ancestor = go_2_ancestor
+  )
+
+  # check output against snap reference
+  withr::with_tempfile("tf", {
+    # save output to tempfile
+    write.table(out, file = tf,
+                sep = "\t", row.names = FALSE, col.names = TRUE)
+
+    expect_snapshot_file(tf, "expand-terms.txt")
+  })
+})
+
+## Generate some data to test other GO term functions
+# get some significantly enriched proteins
+dep_filt <- dep_results %>%
+  distinct(ensembl, .keep_all = TRUE)
+
+enriched <- dep_filt %>%
+  mutate(sig_inc = Ubi4_vs_Ctrl_ratio > 0 & Ubi4_vs_Ctrl_p.adj < 0.05) %>%
+  dplyr::select(ensembl, sig_inc) %>%
+  tibble::deframe()
+
+# make some fake bias data for generating pwf
+set.seed(1234)
+bias <- sample(1:25, size = length(enriched), replace = TRUE)
+
+# generate pwf
+pwf <- goseq::nullp(enriched, bias.data = bias, plot.fit = FALSE)
+
+test_that("get_enriched_go() works when gene2cat is NULL", {
+  # test when gene2cat is not provided
+  out <- get_enriched_go(
+    pwf = pwf,
+    gene2cat = NULL
+  )
+
+  # check output against snap reference
+  withr::with_tempfile("tf", {
+    # save output to tempfile
+    write.table(out, file = tf,
[…]

### 2022-04-07 R/go.R
Fix failing GO tests
In a way that doesn't require adding the rather
massive org.Hs.eg.db package to Suggests.

@@ -464,7 +464,7 @@ remove_redundant_go <- function(obj) {
 #' and plot more than 100 GO terms.
 #'
 #' @param obj `data.frame` containing `goseq` results as generated by
-#' \code{\link{get_enriched_go}} then \code{\link[goseq]{estimate_go_overrep}}.
+#' \code{\link{get_enriched_go}} then \code{\link{estimate_go_overrep}}.
 #' See below for an example.
 #' @param term_col `character` column name for GO term description.
 #' @param ontology_col `character` column name for GO term ontology.
@@ -514,14 +514,14 @@ plot_go <- function(obj,
 
   # construct y axis text
   to_plot <- obj %>%
-    arrange(desc(over_represented_adj_pval)) %>%
+    arrange(desc(.data$over_represented_adj_pval)) %>%
     mutate(term_ontology = paste0(!!sym(term_col), ' (', !!sym(ontology_col), ')')) %>%
-    mutate(term_ontology = factor(term_ontology, levels = term_ontology))
+    mutate(term_ontology = factor(.data$term_ontology, levels = .data$term_ontology))
 
   # construct plot
   p <- to_plot %>%
-    ggplot(aes(x = adj_overrep, y = term_ontology,
-               fill = -log10(over_represented_adj_pval))) +
+    ggplot(aes(x = .data$adj_overrep, y = .data$term_ontology,
+               fill = -log10(.data$over_represented_adj_pval))) +
     geom_bar(stat = 'identity') +
     theme_camprot(base_size = 15, border = FALSE) +
     scale_fill_continuous(limits = c(0, NA),
@@ -536,7 +536,7 @@ plot_go <- function(obj,
          fill = "-log10(FDR)")
 
   if (annotate_n) {
-    p <- p + geom_text(aes(label = numDEInCat),
+    p <- p + geom_text(aes(label = .data$numDEInCat),
                        x = max(to_plot$adj_overrep)*1.2, hjust = 1) +
       xlim(NA, max(to_plot$adj_overrep)*1.2)
   }

### 2022-04-07 tests/testthat/test-go.R

@@ -52,11 +52,11 @@ bias <- sample(1:25, size = length(enriched), replace = TRUE)
 # generate pwf
 pwf <- goseq::nullp(enriched, bias.data = bias, plot.fit = FALSE)
 
-test_that("get_enriched_go() works when gene2cat is NULL", {
-  # test when gene2cat is not provided
+test_that("get_enriched_go() works", {
+  # use dep_gene2cat which is installed with camprotR
   out <- get_enriched_go(
     pwf = pwf,
-    gene2cat = NULL
+    gene2cat = dep_gene2cat
   )
 
   # check output against snap reference
@@ -65,42 +65,21 @@ test_that("get_enriched_go() works when gene2cat is NULL", {
     write.table(out, file = tf,
                 sep = "\t", row.names = FALSE, col.names = TRUE)
 
-    expect_snapshot_file(tf, "get-enriched-go-null-input.txt")
-  })
-})
-
-# obtain GO terms annotated to enriched proteins (just for test purposes)
-gene_2_cat <- goseq::getgo(dep_filt$ensembl, genome = "hg19", id = "ensGene",
-                           fetch.cats=c("GO:CC", "GO:BP", "GO:MF"))
-
-test_that("get_enriched_go() works if gene2cat is provided", {
-  # test when gene2cat is provided
-  out <- get_enriched_go(
-    pwf = pwf,
-    gene2cat = gene_2_cat
-  )
-
-  # check output against snap reference
-  withr::with_tempfile("tf", {
-    # save output to tempfile
-    write.table(out, file = tf,
-                sep = "\t", row.names = FALSE, col.names = TRUE)
-
-    expect_snapshot_file(tf, "get-enriched-go-std-input.txt")
+    expect_snapshot_file(tf, "get-enriched-go.txt")
   })
 })
 
 test_that("estimate_go_overrep() works", {
   go_res <- get_enriched_go(
     pwf = pwf,
-    gene2cat = gene_2_cat
+    gene2cat = dep_gene2cat
   )
 
   # does it work when gene2cat is named list?
   out <- estimate_go_overrep(
     obj = go_res,
     pwf = pwf,
-    gene2cat = gene_2_cat
+    gene2cat = dep_gene2cat
   )
 
   # check output against snap reference
@@ -112,7 +91,7 @@ test_that("estimate_go_overrep() works", {
[…]

### 2022-04-08 tests/testthat/test-go.R
Use less decimals in GO snaps

@@ -57,7 +57,8 @@ test_that("get_enriched_go() works", {
   out <- get_enriched_go(
     pwf = pwf,
     gene2cat = dep_gene2cat
-  )
+  ) %>%
+    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -80,7 +81,8 @@ test_that("estimate_go_overrep() works", {
     obj = go_res,
     pwf = pwf,
     gene2cat = dep_gene2cat
-  )
+  ) %>%
+    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -101,7 +103,8 @@ test_that("estimate_go_overrep() works", {
     obj = go_res,
     pwf = pwf,
     gene2cat = gene_2_cat_df
-  )
+  ) %>%
+    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -128,7 +131,8 @@ test_that("remove_redundant_go() works", {
 
   out <- go_res %>%
     filter(grepl("immune", term)) %>%
-    remove_redundant_go()
+    remove_redundant_go() %>%
+    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
 
   # check output against snap reference
   withr::with_tempfile("tf", {

### 2022-04-08 tests/testthat/test-go.R
Reduce decimals in different way
I hate decimals!

@@ -19,20 +19,14 @@ test_that("expand_terms() works", {
   names(go_2_ancestor) <- go_df$GO.ONT
 
   # run `expand_terms()` to test and capture output
-  out <- expand_terms(
-    go_df = go_df,
-    go_col = "GO.ID",
-    go2Ancestor = go_2_ancestor
-  )
-
   # check output against snap reference
-  withr::with_tempfile("tf", {
-    # save output to tempfile
-    write.table(out, file = tf,
-                sep = "\t", row.names = FALSE, col.names = TRUE)
-
-    expect_snapshot_file(tf, "expand-terms.txt")
-  })
+  expect_snapshot(
+    expand_terms(
+      go_df = go_df,
+      go_col = "GO.ID",
+      go2Ancestor = go_2_ancestor
+    )
+  )
 })
 
 ## Generate some data to test other GO term functions
@@ -58,7 +52,7 @@ test_that("get_enriched_go() works", {
     pwf = pwf,
     gene2cat = dep_gene2cat
   ) %>%
-    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
+    select(category, term)
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -82,7 +76,8 @@ test_that("estimate_go_overrep() works", {
     pwf = pwf,
     gene2cat = dep_gene2cat
   ) %>%
-    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
+    select(category, term, adj_overrep) %>%
+    mutate(adj_overrep = round(adj_overrep, digits = 3))
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -104,7 +99,8 @@ test_that("estimate_go_overrep() works", {
     pwf = pwf,
     gene2cat = gene_2_cat_df
   ) %>%
-    mutate(across(matches("pval"), format, digits = 4, nsmall = 2))
+    select(category, term, adj_overrep) %>%
+    mutate(adj_overrep = round(adj_overrep, digits = 3))
 
   # check output against snap reference
   withr::with_tempfile("tf", {
@@ -112,7 +108,7 @@ test_that("estimate_go_overrep() works", {
     write.table(out2, file = tf,
                 sep = "\t", row.names = FALSE, col.names = TRUE)
 
-    expect_snapshot_file(tf, "estimate-go-overrep-list-input.txt")
[…]

### 2022-04-13 R/rbps.R
Ts add lfq vignette (#42)
* adds LFQ vignette

* finalises LFQ vignette to protein inference

* updates normalise to ref

* finalises first draft LFQ vignette

* resolve dependencies

* resolve dependencies(2)

* clarifies missing heatmap colours

* Query UniProt directly in LFQ vignette

UniProt.ws is not great. Now we just query the
UniProt REST API directly using the `httr` package.

Also other small changes to MSnSet construction
and other code in LFQ vignette.

* iq is back on CRAN: https://github.com/tvpham/iq/issues/2

* Finish CSD review of LFQ vignette

* Put back filter using pData

@@ -1,0 +1,11 @@
+#' RNA-binding proteins
+#'
+#' @description List of RNA binding proteins for use in LFQ vignette
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#'
+#' @keywords datasets
+"rbps"

### 2022-04-14 R/lfq_oops_rnase.R
updates LFQ vignette for re-exported data

@@ -9,5 +9,18 @@
 #' }
 #'
 #' @keywords datasets
-"lfq_oops_rnase"
+"lfq_oops_rnase_pep"
+
+#' PSM PD output for LFQ of RNase +/- OOPS experiment
+#'
+#' @description OOPS CL vs NC
+#' F17-20 = RNase(-) reps 1-4
+#' F21-24 = RNase(+) reps 1-4
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @keywords datasets
+"lfq_oops_rnase_psm"
 

### 2022-04-14 data-raw/lfq_oops_rnase.R

@@ -1,0 +1,18 @@
+# Load libraries
+library(dplyr)
+
+# All files from https://github.com/CambridgeCentreForProteomics/RBPMap_RNase/tree/master/pilot_3/raw/reexport
+# Read in PSM data
+lfq_oops_rnase_pep <- read.delim(
+  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt")
+)
+
+# Output .rda file
+usethis::use_data(lfq_oops_rnase_pep)
+
+lfq_oops_rnase_psm <- read.delim(
+  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PSMs.txt")
+)
+
+# Output .rda file
+usethis::use_data(lfq_oops_rnase_psm)

### 2022-04-14 data-raw/lfq_rbpmap.R

@@ -1,15 +1,0 @@
-# Load libraries
-library(dplyr)
-
-# All files from https://github.com/CambridgeCentreForProteomics/RBPMap_RNase/tree/master/pilot_3/raw
-# Read in PSM data
-'./data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt'
-lfq_oops_rnase <- read.delim(
-  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt")
-)
-
-# Adding an artifical protein accessions column as this is needed for camprotR::parse_features
-lfq_oops_rnase$Protein.Accessions <- lfq_oops_rnase$Master.Protein.Accessions
-
-# Output .rda file
-usethis::use_data(lfq_oops_rnase)

### 2022-04-19 R/silac_psm_seq_int.R
attempts to resolve R CMD check warnings

@@ -54,11 +54,12 @@ silac_psm_seq_int <- function(
              !!sym(mod_col)) %>%
     tally() %>%
     mutate('matched'=TRUE) %>%
-    pivot_wider(names_from=Quan.Channel, values_from=c(n, matched)) %>%
-    mutate(n_Light=replace_na(n_Light, 0),
-           n_Heavy=replace_na(n_Heavy, 0),
-           matched_Light=replace_na(matched_Light, FALSE),
-           matched_Heavy=replace_na(matched_Heavy, FALSE))
+    pivot_wider(names_from=.data$Quan.Channel,
+                values_from=c(.data$n, .data$matched)) %>%
+    mutate(n_Light=replace_na(.data$n_Light, 0),
+           n_Heavy=replace_na(.data$n_Heavy, 0),
+           matched_Light=replace_na(.data$matched_Light, FALSE),
+           matched_Heavy=replace_na(.data$matched_Heavy, FALSE))
 
   if(include_interference){
 

### 2022-04-19 data-raw/lfq_oops_rnase.R
updates LFQ vignette for reduced input

@@ -7,12 +7,19 @@ lfq_oops_rnase_pep <- read.delim(
   here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt")
 )
 
+random_proteins <- sample(unique(lfq_oops_rnase_pep$Master.Protein.Accessions), 100)
+lfq_oops_rnase_pep <- lfq_oops_rnase_pep %>% filter(Master.Protein.Accessions %in% random_proteins)
+
+
 # Output .rda file
-usethis::use_data(lfq_oops_rnase_pep)
+usethis::use_data(lfq_oops_rnase_pep, overwrite=TRUE)
 
 lfq_oops_rnase_psm <- read.delim(
   here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PSMs.txt")
 )
 
+
+lfq_oops_rnase_psm <- lfq_oops_rnase_psm %>% filter(Master.Protein.Accessions %in% random_proteins)
+
 # Output .rda file
-usethis::use_data(lfq_oops_rnase_psm)
+usethis::use_data(lfq_oops_rnase_psm, overwrite=TRUE)

### 2022-04-19 R/glycoproteins.R
clearing up docs and data

@@ -1,11 +1,0 @@
-#' Glycoproteoins
-#'
-#' @description data.fram with glycoproteins for use in LFQ vignette
-#'
-#' \describe{
-#'   \item{column name}{`class`. Description.}
-#' }
-#'
-#'
-#' @keywords datasets
-"glycoproteins"

### 2022-04-19 R/rbps.R

@@ -1,11 +1,0 @@
-#' RNA-binding proteins
-#'
-#' @description List of RNA binding proteins for use in LFQ vignette
-#'
-#' \describe{
-#'   \item{column name}{`class`. Description.}
-#' }
-#'
-#'
-#' @keywords datasets
-"rbps"

### 2022-04-19 R/estimate_incorporation.R
updates LFQ vignette for re-exported data (#46)
* updates silac_psm_seq_int to more informative output (#38)

* updates silac_psm_seq_int to more informative output

* updates docs

* debug SILAC vignette

Co-authored-by: TomSmithCGAT <tss38@mrc-tox.cam.ac.uk>

* Ts add lfq vignette (#42)

* adds LFQ vignette

* finalises LFQ vignette to protein inference

* updates normalise to ref

* finalises first draft LFQ vignette

* resolve dependencies

* resolve dependencies(2)

* clarifies missing heatmap colours

* Query UniProt directly in LFQ vignette

UniProt.ws is not great. Now we just query th

@@ -117,6 +117,7 @@ estimate_incorporation <- function(
     psm_input,
     sequence_col = sequence_col,
     mod_col = modifications_col,
+    include_interference = TRUE,
     interference_col = "Isolation.Interference.in.Percent"
   )
 
@@ -188,7 +189,7 @@ estimate_incorporation <- function(
 
   # make columns indicating if peptide was identified by PSM or by mass shift
   merged_data$Found.Light <- ifelse(
-    merged_data$Sequenced_Light, "Light: Spectrum matched",
+    merged_data$matched_Light, "Light: Spectrum matched",
     ifelse(
       is.finite(merged_data$Light), "Light: Detected by mass shift",
       "Light: Not found"
@@ -196,7 +197,7 @@ estimate_incorporation <- function(
   )
 
   merged_data$Found.Heavy <- ifelse(
-    merged_data$Sequenced_Heavy, "Heavy: Spectrum matched",
+    merged_data$matched_Heavy, "Heavy: Spectrum matched",
     ifelse(
       is.finite(merged_data$Heavy), "Heavy: Detected by mass shift",
       "Heavy: Not found"

### 2022-04-19 R/lfq_oops_rnase.R

@@ -1,0 +1,26 @@
+#' PeptideGroups PD output for LFQ of RNase +/- OOPS experiment
+#'
+#' @description OOPS CL vs NC
+#' F17-20 = RNase(-) reps 1-4
+#' F21-24 = RNase(+) reps 1-4
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @keywords datasets
+"lfq_oops_rnase_pep"
+
+#' PSM PD output for LFQ of RNase +/- OOPS experiment
+#'
+#' @description OOPS CL vs NC
+#' F17-20 = RNase(-) reps 1-4
+#' F21-24 = RNase(+) reps 1-4
+#'
+#' \describe{
+#'   \item{column name}{`class`. Description.}
+#' }
+#'
+#' @keywords datasets
+"lfq_oops_rnase_psm"
+

### 2022-04-19 R/silac_psm_seq_int.R

@@ -2,26 +2,34 @@
 #' PSM-level output
 #'
 #' @description Proteome Discoverer does not correctly propagate from PSM to
-#' peptide level output which intensities are from "sequenced" peptides, e.g MS2
+#' peptide level output which intensities are from "matched" peptides, e.g MS2
 #' fragmentation. This information is useful to assess the accuracy of
-#' quantification in peptides identified by mass shift relative to a sequenced
+#' quantification in peptides identified by mass shift relative to a matched
 #' peptide in SILAC experiments
 #'
 #' @param obj `data.frame` PSM-level output from Proteome Discoverer
 #' @param sequence_col `string` Column with peptide sequence
 #' @param mod_col `string` Column with modifications
+#' @param include_interference `logical` Should PSM interference be included too?
 #' @param interference_col `string` Column with interference/co-isolation
-#' @return `data.frame` indicating which SILAC peptides were MS2 sequenced and
-#' the maximum interference across all PSMs for the peptide
+#' @return `data.frame` indicating which SILAC peptides were MS2 matched,
+#' how many PSMs per isotope, and
+#' (optionally) the maximum interference across all PSMs for the peptide
 #' @export
 silac_psm_seq_int <- function(
   obj,
   sequence_col='Sequence',
   mod_col='Modifications',
+  include_interference=FALSE,
   interference_col='Isolation.Interference.in.Percent'){
 
+  message('camprotR::silac_psm_seq_int output has changed.
+  Columns indicating whether quantification is from PSM are now prefixed with
+  "matched", not "Sequenced", and tallys of PSMs per isotope are included.
+  Interference is not included by default (set include_interference=TRUE)')
+
   # check that input files have the necessary columns
-  required_cols <- c(sequence_col, mod_col, interference_col,
+  required_cols <- c(sequence_col, mod_col,
                      "Quan.Channel", "Precursor.Abundance")
 
   if (!all(required_cols %in% colnames(obj))) {
@@ -42,18 +50,31 @@ silac_psm_seq_int <- function(
   obj[[sequence_col]] <- toupper(obj[[sequence_col]])
 
   obj_seq <- obj %>%
-    group_by(!!sym(sequence_col), .data$Quan.Channel, !!sym(mod_col)) %>%
[…]

### 2022-04-19 data-raw/lfq_oops_rnase.R

@@ -1,0 +1,25 @@
+# Load libraries
+library(dplyr)
+
+# All files from https://github.com/CambridgeCentreForProteomics/RBPMap_RNase/tree/master/pilot_3/raw/reexport
+# Read in PSM data
+lfq_oops_rnase_pep <- read.delim(
+  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PeptideGroups.txt")
+)
+
+random_proteins <- sample(unique(lfq_oops_rnase_pep$Master.Protein.Accessions), 100)
+lfq_oops_rnase_pep <- lfq_oops_rnase_pep %>% filter(Master.Protein.Accessions %in% random_proteins)
+
+
+# Output .rda file
+usethis::use_data(lfq_oops_rnase_pep, overwrite=TRUE)
+
+lfq_oops_rnase_psm <- read.delim(
+  here::here("data-raw/RBPMap_RNase_pilot_3/LFQ_OOPS_RNase_MetChloroform-(1)_PSMs.txt")
+)
+
+
+lfq_oops_rnase_psm <- lfq_oops_rnase_psm %>% filter(Master.Protein.Accessions %in% random_proteins)
+
+# Output .rda file
+usethis::use_data(lfq_oops_rnase_psm, overwrite=TRUE)

### 2022-05-12 R/silac_psm_seq_int.R
adds option to include more grouping columns for silac_psm_seq_int.R (#49)

@@ -12,6 +12,8 @@
 #' @param mod_col `string` Column with modifications
 #' @param include_interference `logical` Should PSM interference be included too?
 #' @param interference_col `string` Column with interference/co-isolation
+#' @param group_cols `string` Additional feature columns to retain, beyond
+#' Sequence and Modification
 #' @return `data.frame` indicating which SILAC peptides were MS2 matched,
 #' how many PSMs per isotope, and
 #' (optionally) the maximum interference across all PSMs for the peptide
@@ -21,7 +23,8 @@ silac_psm_seq_int <- function(
   sequence_col='Sequence',
   mod_col='Modifications',
   include_interference=FALSE,
-  interference_col='Isolation.Interference.in.Percent'){
+  interference_col='Isolation.Interference.in.Percent',
+  group_cols=NULL){
 
   message('camprotR::silac_psm_seq_int output has changed.
   Columns indicating whether quantification is from PSM are now prefixed with
@@ -49,9 +52,14 @@ silac_psm_seq_int <- function(
 
   obj[[sequence_col]] <- toupper(obj[[sequence_col]])
 
+  if(!missing(group_cols)){
+    group_cols <- c(group_cols, 'Quan.Channel')
+  } else{
+    group_cols <- 'Quan.Channel'
+  }
+
   obj_seq <- obj %>%
-    group_by(!!sym(sequence_col), .data$Quan.Channel,
-             !!sym(mod_col)) %>%
+    group_by(across(all_of(c(sequence_col, group_cols, mod_col)))) %>%
     tally() %>%
     mutate('matched'=TRUE) %>%
     pivot_wider(names_from=.data$Quan.Channel,

### 2022-09-05 R/make_fasta.R
Hotfix for UniProt queries
Fix functions/vignette that query the old
UniProt REST API.

@@ -29,42 +29,75 @@
 make_fasta <- function(accessions, file, is_crap = FALSE, overwrite = FALSE, verbose = TRUE) {
   # define payload used to query uniprot
   payload <- list(
-    query = paste(accessions, collapse = " "),
-    from = "ACC+ID",
-    to = "ACC",
-    format = "fasta"
+    ids = paste(accessions, collapse = " "),
+    from = "UniProtKB_AC-ID",
+    to = "UniProtKB"
   )
 
-  # query uniprot and save FASTA to disk
-  # security level fix for Ubuntu 20.04
-  # see https://msmith.de/2020/10/02/httr-curl-ubuntu-20-04.html
-  httr_config <- switch(
-    Sys.info()["sysname"],
-    "Linux" = httr::config(ssl_cipher_list = "DEFAULT@SECLEVEL=1"),
-    httr::config()
-  )
+  # submit job
+  post_payload <- httr::POST(url = "https://rest.uniprot.org/idmapping/run",
+                             body = payload, encode = "multipart", httr::accept_json())
 
-  response <- httr::with_config(
-    config = httr_config,
-    httr::GET(
-      url = "https://www.uniprot.org/uploadlists/",
-      query = payload,
-      config = httr::write_disk(path = file, overwrite = overwrite)
-    )
-  )
-
-  # basic http error handling
-  httr::stop_for_status(response, "query UniProt")
+  post_resp <- httr::content(post_payload, as = "parsed")
 
   # print UniProtKB release
   if (verbose) message(paste("Downloading from UniProtKB release:",
-                             response$headers$`x-uniprot-release`))
+                             post_payload$headers$`x-uniprot-release`))
+
+  # check status of job
+  if (isTRUE(check_uniprot_job(post_resp[["jobId"]]))) {
+    result_url <- paste("https://rest.uniprot.org/idmapping/uniprotkb/results/stream/", post_resp[["jobId"]], sep = "")
+
+    # query uniprot and save FASTA to disk
+    # security level fix for Ubuntu 20.04
+    # see https://msmith.de/2020/10/02/httr-curl-ubuntu-20-04.html
+    httr_config <- switch(
+      Sys.info()["sysname"],
+      "Linux" = httr::config(ssl_cipher_list = "DEFAULT@SECLEVEL=1"),
+      httr::config()
+    )
+
+    response <- httr::with_config(
+      config = httr_config,
+      httr::GET(
[…]

### 2022-11-08 README.Rmd
Update README

@@
 ```{r, eval=FALSE}
-remotes::install_github("CambridgeCentreForProteomics/camprotR", build_vignettes = TRUE)
+remotes::install_github("CambridgeCentreForProteomics/camprotR", dependencies = TRUE)
 ```
@@
 
-Several HTML vignettes are installed with this package which go through how to
-use different aspects of the package. You can see a list of available vignettes
-with:
-
-```{r, eval=FALSE}
-browseVignettes("camprotR")
-```
+Vignettes which go through how to use different aspects of the package are 
+available on the `camprotR` website [here](https://cambridgecentreforproteomics.github.io/camprotR/) (see Articles tab).
